---
title: "V2 Analysis"
author: "Michelle"
date: "April 19, 2024"
output:
  html_document:
    toc: true
    toc_float: true
---
---

Check all files that have carried over from the backup.

Data:
master_dataset: N=619065, long format, 1960-2023
scm_data: N=1820, wide format, 2010-2023 — 00s appear for 2023 observations
scm_data2: N=1440, wide format, 2010-2022 (except Afghanistan, which ends at 2021?) — no NAs
—> copying scm_data2 to new data folder

---

Select most complete dataset (scm_data2) and import here
```{r data1}
library(readr)
data <- read_csv("data/scm_data2 copy.csv")
```

Verify the following features
- years available
- countries available
- variables available
```{r data2}
library(dplyr)

data <- data %>%
  select(-flights.spike.true, -passengers.spike.true, -Intervention, -`...1`)

unique_years <- unique(data$year)
unique_countries <- unique(data$Country.Name)
variable_list <- names(data)

unique_years
unique_countries
variable_list
```

We're missing some countries and variables that didn't carry over. I fixed this before, but didn't back it up. Let's pause and take care of that.
- GDP in international dollars 2017

Missing some key variables:
- total FDI
- logs/lags on some variables (can be generated during the analysis)
```{r data3}

```


Graph: FDI graphed against passengers (controlling for deaths) 
```{r}
ggplot(data, aes(x = passengers.in.change.pct, y = FDI)) +
  geom_point() +
  labs(x = "Passengers Change (%)", y = "FDI (Foreign Direct Investment)")
```

identify outliers
comment on shape of data

Graph: FDI graphed against deaths (controlling for FDI).
identify outliers
comment on shape of data

Consider: what models would be best?

Regenerate DID to verify
- comment on any changes and why. 
- is this acceptable, are we good to move forward? 

Report results with both 25+ and 50+ ACLED deaths. 

Regressions with more lags. Focus on natural logs...