---
title: 'Running Models'
author: "Michelle Schultze"
date: "2024-05-17"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(readr)
library(readxl)
library(naniar)
#install.packages("readr", repos = "http://cran.us.r-project.org")
#install.packages("microsynth", repos = "http://cran.us.r-project.org")
#install.packages("LowRankQP", repos = "http://cran.us.r-project.org")
library("readr")
library("microsynth")
library("LowRankQP")

setwd('/Users/michelleschultze/ukr2024')
data <- read_csv("data/NEWDATA_May172024.csv")
```

[Descriptive stats will go here]

We have some outliers with Hungary (2018) and Azerbaijan (2014) with high spikes in passengers flying into the country. This seems to be measurement error. Let's cut them from the dataset.
```{r filter message=FALSE, warning=FALSE}
data <- data %>% 
  filter(Country.Name != "Azerbaijan",
         Country.Name != "Hungary")
```


Models we would like to run:

No FE: 
(1a) log(total FDI) = lag(percentage change in passengers flying in)
(2a) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(ACLED battle deaths))
(3a) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(total GDP)) + lag(log(ACLED battle deaths))
(4a) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(ACLED battle deaths)) + lag(log(GDP per capita, PPP))
(5a) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(total GDP)) + lag(log(ACLED battle deaths)) + lag(log(GDP per capita, PPP))

W/ Country FE:
(3b) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(total GDP)) + lag(log(ACLED battle deaths)) + FE
(4b) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(ACLED battle deaths)) + lag(log(GDP per capita, PPP)) + FE
(5b) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(total GDP)) + lag(log(ACLED battle deaths)) + lag(log(GDP per capita, PPP)) + FE

Add in PPP GDP & per capita measures from WB
```{r ppp, message=FALSE, warning=FALSE}
#deleted header rows with metadata to allow for import
ppp_pc <- read_csv("data/gdp_ppp_per capita.csv")
ppp <- read_csv("data/gdp_ppp.csv")

#let's pivot and merge these together
ppp <- ppp %>%
  pivot_longer(cols = where(is.numeric), names_to = "year") %>%
  filter(!is.na(value)) %>%
  select(1,3, year, value)

ppp_pc <- ppp_pc %>%
  pivot_longer(cols = where(is.numeric), names_to = "year") %>%
  filter(!is.na(value)) %>%
  select(1,3, year, value)

ppp <- ppp %>% 
  full_join(ppp_pc)

colnames(ppp) <- c("Country.Name", "Indicator.Name", "year", "value")

ppp <- ppp %>%
  pivot_wider(names_from = Indicator.Name, values_from = value) %>%
  group_by(Country.Name, year) %>%
  summarise_all(~ if (any(!is.na(.))) .[!is.na(.)][1] else NA) %>%
  mutate(year = as.numeric(year))

#standardize names:
ppp <- ppp %>%
  mutate(Country.Name = case_when(
    Country.Name == "Democratic Republic of the Congo" ~ "Congo, Dem. Rep.",
    Country.Name == "Congo" ~ "Congo, Dem. Rep.",
    Country.Name == "Bahamas" ~ "Bahamas, The",
    Country.Name == "Cape Verde" ~ "Cabo Verde",
    Country.Name == "Czech Republic" ~ "Czechia",
    Country.Name == "East Timor" ~ "Timor-Leste",
    Country.Name == "Egypt" ~ "Egypt, Arab Rep.",
    Country.Name == "Gambia" ~ "Gambia, The", 
    Country.Name == "Guinea Bissau" ~ "Guinea-Bissau",
    Country.Name == "Iran" ~ "Iran, Islamic Rep.",
    Country.Name == "Ivory Coast (Cote d'Ivoire)" ~ "Cote d'Ivoire",
    Country.Name == "Kyrgyzstan" ~ "Kyrgyz Republic", 
    Country.Name == "Laos" ~ "Lao PDR",
    Country.Name == "Macedonia" ~ "North Macedonia",
    Country.Name == "Micronesia" ~ "Micronesia, Fed. Sts.",
    Country.Name == "North Korea" ~ "Korea, Dem. People's Rep.", 
    Country.Name == "Saint Kitts and Nevis" ~ "St. Kitts and Nevis",
    Country.Name == "Saint Lucia" ~ "St. Lucia",
    Country.Name == "Saint Vincent and Grenadines" ~ "St. Vincent and the Grenadines",
    Country.Name == "Saint Vincent and the Grenadines" ~ "St. Vincent and the Grenadines",
    Country.Name == "Slovakia" ~ "Slovak Republic",
    Country.Name == "South Korea" ~ "Korea, Rep.",
    Country.Name == "Swaziland" ~ "Eswatini",
    Country.Name == "Syria" ~ "Syrian Arab Republic",
    Country.Name == "Yemen" ~ "Yemen, Rep.",
    Country.Name == "Vietnam" ~ "Viet Nam",
    Country.Name == "Venezuela" ~ "Venezuela, RB",
    Country.Name == "Turkey" ~ "Turkiye",
    Country.Name == "Hong Kong (SAR)" ~ "Hong Kong SAR, China",
    Country.Name == "Macau (SAR)" ~ "Macao SAR, China",
    Country.Name == "Brunei" ~ "Brunei Darussalam",
    Country.Name == "West Bank and Gaza" ~ "Palestine",
    Country.Name == "Saint Martin" ~ "St. Martin (French part)",
    Country.Name == "Saint-Martin" ~ "St. Martin (French part)",
    Country.Name == "Sint Maarten" ~ "Sint Maarten (Dutch part)",
    Country.Name == "Saint-Barthelemy" ~ "Saint Barthelemy",
    Country.Name == "Russian Federation" ~ "Russia",
    Country.Name == "Iran, Islamic Rep." ~ "Iran",
    Country.Name == "Brunei Darussalam" ~ "Brunei",
    Country.Name == "Congo (Kinshasa)" ~ "Congo, Dem. Rep.",
    Country.Name == "Congo (Brazaville)" ~ "Congo, Rep.",
    Country.Name == "Democratic Republic of Congo" ~ "Congo, Dem. Rep.",
    Country.Name == "Republic of Congo" ~ "Congo, Rep.",
    Country.Name == "Czech Republic" ~ "Czechia",
    Country.Name == "Egypt, Arab Rep." ~ "Egypt",
    Country.Name == "Hong Kong SAR, China" ~ "Hong Kong",
    Country.Name == "Ivory Coast" ~ "Cote d'Ivoire",
    Country.Name == "Lao PDR" ~ "Laos", 
    Country.Name == "Macao SAR, China" ~ "Macau",
    Country.Name == "Macedonia" ~ "North Macedonia",
    Country.Name == "Slovak Republic" ~ "Slovakia",
    Country.Name == "South Korea" ~ "Korea, Rep.",
    Country.Name == "North Korea" ~ "Korea, Dem. People's Rep.",
    Country.Name == "Syrian Arab Republic" ~ "Syria",
    Country.Name == "Turkey" ~ "Turkiye",
    Country.Name == "Venezuela, RB" ~ "Venezuela",
    Country.Name == "Viet Nam" ~ "Vietnam",
    Country.Name == "Kyrgyz Republic" ~ "Kyrgyzstan",
    Country.Name == "Yemen, Rep." ~ "Yemen",
    TRUE ~ Country.Name)
  ) %>%
  filter(!(Country.Name %in% c("European Union", "Latin America & Caribbean", "Latin America & Caribbean (excluding high income)", "South Asia", "Sub-Saharan Africa (excluding high income)", "Grenada and South Grenadines", "Saint Helena, Ascension and Tristan da Cunha", "U.S.S.R.", "West Germany"))) 
  #no need to delete aggregated entities (ie. "West Africa") — they'll drop when we merge with the main dataframe!

data <- data %>%
  left_join(ppp, by = c("Country.Name", "year"))
```

Create some logged variables:
```{r vars, message=FALSE, warning=FALSE}
data <- data %>% 
  mutate(total_FDI_n = Foreign.direct.investment.net.inflows.pct.of.GDP * `GDP.current.US$`,
         total_FDI_r = Foreign.direct.investment.net.inflows.pct.of.GDP * `GDP, PPP (current international $)`,
    log_FDI_n = log1p(total_FDI_n),
    log_FDI_r = log1p(total_FDI_r),
    log_GDP_n = log1p(`GDP.current.US$`),
    log_GDP_r = log1p(`GDP, PPP (current international $)`),
    log_GDP_r_pc = log1p(`GDP per capita, PPP (current international $)`),
    log_battle = log1p(fatalities.y.Battles))
```

Guide to new variables:
total_FDI_n = nominal total FDI (from nominal GDP numbers in current $US)
total_FDI_r = real total FDI (from PPP GDP numbers in current $US)
log_FDI_n = nominal total FDI, logged+1
log_FDI_r = real total FDI, logged+1
log_GDP_n = nominal GDP, logged+1
log_GDP_r = real GDP, logged+1
log_GDP_r_pc = real GDP per capita, logged+1
log_battle = battle fatalities, logged+1

MODELS WITHOUT FIXED EFFECTS

(1a) log(total FDI) = lag(percentage change in passengers flying in)
```{r model.1a, message=TRUE, warning=TRUE}
model.1a <- lm(log_FDI_n ~ lag(passengers.in.change.pct), data = data)
summary(model.1a)
```
Model 1a is the most basic model, yet we see the coefficient of interest is not significant.

(2a) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(ACLED battle deaths))
```{r model.2a, message=TRUE, warning=TRUE}
model.2a <- lm(log_FDI_n ~ lag(passengers.in.change.pct) + lag(log_battle), data = data)
summary(model.2a)
```
Model 2a adds battle deaths as a covariate. Passengers is still not significant.

(3a) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(total GDP)) + lag(log(ACLED battle deaths))
```{r model.3a, message=TRUE, warning=TRUE}
model.3a <- lm(log_FDI_n ~ lag(passengers.in.change.pct) + lag(log_battle) + lag(log_GDP_n), data = data)
summary(model.3a)
```
Model 3a adds nominal GDP as a covariate. Passengers is still not significant.

(4a) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(ACLED battle deaths)) + lag(log(GDP in PPP terms))
```{r model.4a, message=TRUE, warning=TRUE}
model.4a <- lm(log_FDI_n ~ lag(passengers.in.change.pct) + lag(log_battle) + lag(log_GDP_r), data = data)
summary(model.4a)
```
Instead of nominal GDP, Model 4a adds real GDP as a covariate. The passengers variable is significant at the 10% level. This is likely because controlling for the real value of the local currency the year before helps to explain much of the variation in FDI the following year.

Model 4a demonstrates that, other factors held constant, a 1% increase in passengers from one year is associated with a 0.0011399% increase (+0.114%) in nominal FDI the following year. 
Scaling up, this means a 100% increase in passengers is associated with a 11.399% increase in nominal FDI the following year!

(5a) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(total GDP)) + lag(log(ACLED battle deaths)) + lag(log(GDP per capita, PPP))
```{r model.5a, message=TRUE, warning=TRUE}
model.5a <- lm(log_FDI_n ~ lag(passengers.in.change.pct) + lag(log_battle) + lag(log_GDP_r_pc), data = data)
summary(model.5a)
```
Including per capita real GDP instead makes the passengers variable insignificant again.
Does this effect carry over when we run it with nominal GDP AND per capita real GDP instead?
```{r model.6a, message=TRUE, warning=TRUE}
model.6a <- lm(log_FDI_n ~ lag(passengers.in.change.pct) + lag(log_battle) + lag(log_GDP_r_pc) + lag(log_GDP_n), data = data)
summary(model.6a)
```
Yes. It looks like controlling for per capita GDP soaks up much of the variation regarding total FDI maybe because it is a population-weighted variable. 
[do more thinking about this]



To be added:

W/ Country FE:
(3b) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(total GDP)) + lag(log(ACLED battle deaths)) + FE


(4b) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(ACLED battle deaths)) + lag(log(GDP per capita, PPP)) + FE


(5b) log(total FDI) = lag(percentage change in passengers flying in) + lag(log(total GDP)) + lag(log(ACLED battle deaths)) + lag(log(GDP per capita, PPP)) + FE
