---
title: "Decile Regressions"
author: "Michelle Schultze"
date: "Sept 21, 2024"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---
---

##Data prep

Load in packages.
```{r packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(readr)
library(readxl)
library(naniar)
library("readr")
library("microsynth")
library("LowRankQP")
#install.packages("quantreg")
library(quantreg)
#install.packages("openxlsx")
library(openxlsx)

setwd('/Users/michelle/Documents/ukr2024/Replication files')
data <- read_csv("full_data.csv")
```

Log several variables.
```{r log-vars}
data <- data %>%
  mutate(total_FDI_USD = Foreign.direct.investment.net.inflows.pct.of.GDP * `GDP.current.US$` / 100) %>%
  arrange(-total_FDI_USD)

data2 <- data %>%
  select(Country.Name, year, Foreign.direct.investment.net.inflows.pct.of.GDP, fatalities.y.Battles, fatalities.y.Violence.against.civilians, total.passengers.in, count.events.y.All.types.of.violent.conflict, log_FDI_n, log_GDP_r, passengers.in.change.pct)

data2$ln_pass <- log1p(data2$total.passengers.in)
data2$ln_battle_fatalities <- log1p(data2$fatalities.y.Battles)
data2$ln_pass_pct <- log1p(data2$passengers.in.change.pct / 100)

#data2$ln_pass <- replace(data2$ln_pass, is.infinite(data2$ln_pass) & data2$ln_pass < 0, 0)
#data2$ln_battle_fatalities <- replace(data2$ln_battle_fatalities, is.infinite(data2$ln_battle_fatalities) & data2$ln_battle_fatalities < 0, 0)
#data2$ln_civilian_violence_fatalities <- replace(data2$ln_civilian_violence_fatalities, is.infinite(data2$ln_civilian_violence_fatalities) & data2$ln_civilian_violence_fatalities < 0, 0)
#data2$ln_events <- replace(data2$ln_events, is.infinite(data2$ln_events) & data2$ln_events < 0, 0)
```

```{r specify-function}
# Create a function to extract coefficients with stars
extract_coefficients <- function(summary_output) {
  # Initialize an empty vector to store coefficients
  coef_vector <- character()
  
  # Loop through each set of coefficients
  for (i in 1:length(summary_output)) {
    # Extract coefficients and p-values
    coefficients <- summary_output[[i]]$coefficients[, 1]
    p_values <- summary_output[[i]]$coefficients[, 4]
    
    # Compute stars based on p-values
    stars <- ifelse(p_values < 0.001, "***",
                    ifelse(p_values < 0.01, "**",
                           ifelse(p_values < 0.05, "*",
                                  ifelse(p_values < 0.1, ".", ""))))
    
    # Combine coefficients with stars
    coef_with_stars <- paste0(signif(coefficients, digits = 4), stars)
    
    # Append to the coef_vector
    coef_vector <- c(coef_vector, coef_with_stars)
  }
  
  return(coef_vector)
}

# Create a function to extract coefficients withOUT stars
extract_coefficients_nostars <- function(summary_output) {
  # Initialize an empty vector to store coefficients
  coef_vector <- character()
  
  # Loop through each set of coefficients
  for (i in 1:length(summary_output)) {
    # Extract coefficients and p-values
    coefficients <- summary_output[[i]]$coefficients[, 1]
    p_values <- summary_output[[i]]$coefficients[, 4]
    
    # Combine coefficients with stars
    coef_without_stars <- paste0(signif(coefficients, digits = 4))
    
    # Append to the coef_vector
    coef_vector <- c(coef_vector, coef_without_stars)
  }
  
  return(coef_vector)
}
```

##Decile Regression 1
Decile OLS regression of logged total FDI on logged QUANTITY of passengers flying into a country on US carriers

Log+1 total FDI on log+1 total passengers flying into the country (ln_pass).
```{r A_quantile}
qr.model <- rq(log_FDI_n ~ ln_pass, 
               data = data2, tau = c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1))

qr.model[["coefficients"]]
```

```{r A_extract_coefficients_significance}
summary_output <- summary(qr.model, se = "boot")
coefficients_with_stars <- extract_coefficients(summary_output)
print(coefficients_with_stars)

# Extracted coefficients with tau and variable names
coef_names <- c("Intercept", "ln_pass")
tau_levels <- seq(0.1, 1, by = 0.1)
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)

coef_with_tau <- coef_with_tau %>%
  arrange(as.numeric(tau))

# Combine coefficients with stars and tau information
coef_with_tau$coefficients <- coefficients_with_stars 
```

```{r A_export-to-excel}
#install.packages("openxlsx")
#library(openxlsx)

# Create a data frame to store the formula and weights information
additional_info <- data.frame(
  tau = NA,
  variable = NA,
  coefficients = NA
)

# Add the formula information
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Formula", coefficients = as.character(qr.model$formula)))

# Add the weights information
weights <- ifelse(is.null(qr.model$call$weights), "N/A", as.character(qr.model$call$weights))
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Weights", coefficients = weights))

# Combine the coefficients data frame with the additional information data frame
final_df <- rbind(coef_with_tau, additional_info)

# Specify the file path where you want to save the Excel file
file_path <- "Decile Analysis/Coefficient Tables/exported_tables.xlsx"

# Export the combined data frame to Excel
write.xlsx(final_df, file = file_path, rowNames = FALSE)
```

```{r A_plot_alltaus}
coefficients_without_stars <- extract_coefficients_nostars(summary_output)

coef_names <- c("Intercept", "ln_pass")
tau_levels <- seq(0.1, 1, by = 0.1)
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)

coef_with_tau <- coef_with_tau %>%
  arrange(as.numeric(tau))

# Combine coefficients with stars and tau information
coef_with_tau$coefficients <- coefficients_without_stars 

coef_with_tau <- coef_with_tau %>%
  filter(variable != "Intercept")

# Plotting coefficients against tau
library(ggplot2)
ggplot(coef_with_tau, aes(x = tau, y = as.numeric(coefficients), group = 1)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") + 
  labs(x = "Tau (natural log of passengers flying in on US carriers)", y = "Coefficients (relationship with logged total nominal FDI in terms of $US)", title = "Coefficients vs. Tau") +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1))

ggsave("Decile Analysis/Plots/decile_plotA.jpg", width = 10, height = 5, units = "in", dpi = 300)
```

```{r A_cutoffs}
# Calculate the quantiles for ln_pass
passenger_cutoffs <- quantile(data2$ln_pass, probs = seq(0, 1, by = 0.1))

# Create a data frame for cutoffs
cutoff_df <- data.frame(
  Tau = seq(0, 1, by = 0.1),
  Cutoff = passenger_cutoffs
)

# Create a note for the model variables
model_note <- "Model: Logged total FDI on natural log of passengers flying into the country (ln_pass)."

# Load necessary library for Excel export
library(openxlsx)

# Create a new workbook
new_wb <- createWorkbook()

# Add a worksheet for Tau cutoffs
addWorksheet(new_wb, "Tau_Cutoffs")

# Write the data to the new sheet
writeData(new_wb, sheet = "Tau_Cutoffs", cutoff_df)

# Write the model note at the bottom
writeData(new_wb, sheet = "Tau_Cutoffs", model_note, startRow = nrow(cutoff_df) + 2, colNames = FALSE)

# Save the new workbook
saveWorkbook(new_wb, "Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx", overwrite = TRUE)

# Print the cutoff values for verification
print(cutoff_df)
```


##Decile Regression 2
Decile OLS regression of logged total FDI on PERCENTAGE INCREASE of passengers flying into a country on US carriers

Log+1 total FDI on percent change in passengers flying into the country (passengers.in.change.pct), with country fixed effects.
```{r B_quantile}
qr.model <- rq(log_FDI_n ~ passengers.in.change.pct + factor(Country.Name), 
               data = data2, tau = c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1))

qr.model[["coefficients"]]
```

```{r B_extract_coefficients_significance}
# Extract the summary from the quantile regression model
summary_output <- summary(qr.model, se = "boot")

# Extract the coefficients with significance stars
coefficients_with_stars <- extract_coefficients(summary_output)

# Print the coefficients with stars to check
print(coefficients_with_stars)

# Define the coefficient names and tau levels
coef_names <- c("Intercept", "passengers_in_change_pct")  # Only relevant coefficients
tau_levels <- seq(0.1, 1, by = 0.1)

# Create a data frame to hold tau levels and variable names
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)
coef_with_tau <- coef_with_tau %>% arrange(as.numeric(tau))

# Filter out the country fixed effects (keeping only Intercept and passengers_in_change_pct)
# Adjust the number of coefficients to exclude the fixed effects
num_tau_levels <- length(tau_levels)
num_coefficients <- length(coef_names)
coefficients_filtered <- coefficients_with_stars[1:(num_tau_levels * num_coefficients)]

# Combine the filtered coefficients with the tau information
coef_with_tau$coefficients <- coefficients_filtered

# Print to verify
print(coef_with_tau)
```

```{r B_export-to-excel}
# Create a data frame to store the formula and weights information
additional_info <- data.frame(
  tau = NA,
  variable = NA,
  coefficients = NA
)

# Add the formula information
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Formula", coefficients = as.character(qr.model$formula)))

# Add the weights information
weights <- ifelse(is.null(qr.model$call$weights), "N/A", as.character(qr.model$call$weights))
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Weights", coefficients = weights))

# Combine the coefficients data frame (without fixed effects) with the additional information
final_df <- rbind(coef_with_tau, additional_info)

# Load the existing Excel file
wb <- loadWorkbook("Decile Analysis/Coefficient Tables/exported_tables.xlsx")

# Get the names of existing sheets
sheet_names <- names(wb$worksheets)

# Read the data from the first sheet to determine the starting column
sheet_data <- read.xlsx("Decile Analysis/Coefficient Tables/exported_tables.xlsx", sheet = 1)
current_col <- max(1, ncol(sheet_data) + 1)

# Write the data (coefficients and additional info) to the existing Excel file
writeData(wb, sheet = 1, final_df, startCol = current_col, startRow = 1)

# Save the changes to the Excel file
saveWorkbook(wb, "Decile Analysis/Coefficient Tables/exported_tables.xlsx", overwrite = TRUE)
```

```{r B_plot_alltaus}
# Extract coefficients without stars from the summary output
coefficients_without_stars <- extract_coefficients_nostars(summary_output)

# Filter out the country fixed effects
# Keep only Intercept and passengers_in_change_pct coefficients
num_tau_levels <- length(tau_levels)
num_coefficients <- length(coef_names)
coefficients_filtered <- coefficients_without_stars[1:(num_tau_levels * num_coefficients)]

# Create a dataframe with tau and variable combinations
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)

# Arrange by tau for plotting
coef_with_tau <- coef_with_tau %>%
  arrange(as.numeric(tau))

# Combine coefficients without stars and tau information (only for relevant variables)
coef_with_tau$coefficients <- coefficients_filtered

# Filter out intercept if you want to plot only the variable of interest
coef_with_tau <- coef_with_tau %>%
  filter(variable == "passengers_in_change_pct")

# Load necessary libraries for plotting
library(ggplot2)

# Plot coefficients against tau
ggplot(coef_with_tau, aes(x = tau, y = as.numeric(coefficients), group = 1)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") + 
  labs(x = "Tau (Percent change in passengers flying into the country)", 
       y = "Coefficients (relationship with logged total nominal FDI in terms of $US)", 
       title = "Coefficients vs. Tau",
       subtitle = "With Country Fixed Effects") +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1))

# Save the plot as a .jpg file
ggsave("Decile Analysis/Plots/decile_plotB.jpg", width = 10, height = 5, units = "in", dpi = 300)
```

```{r B_cutoffs}
# Calculate the quantiles for passenger percentage changes
passenger_cutoffs <- quantile(data2$passengers.in.change.pct, probs = seq(0, 1, by = 0.1))

# Create a data frame for cutoffs
cutoff_df <- data.frame(
  Tau = seq(0, 1, by = 0.1),
  Cutoff = passenger_cutoffs
)

# Create a note for the model variables
model_note <- "Model: Logged total FDI on percentage change in passengers flying into the country (passengers.in.change.pct), with country fixed effects."

# Load necessary library for Excel export
library(openxlsx)

# Load the existing workbook for Tau cutoffs
wb <- loadWorkbook("Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx")

# Determine the next available row to insert data
existing_data <- read.xlsx("Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx", sheet = "Tau_Cutoffs")
start_row <- nrow(existing_data) + 3  # Two empty lines before data

# Write the cutoff data to the existing sheet with two empty lines before
writeData(wb, sheet = "Tau_Cutoffs", cutoff_df, startRow = start_row, colNames = TRUE)

# Write the model note at the next row
writeData(wb, sheet = "Tau_Cutoffs", model_note, startRow = start_row + nrow(cutoff_df) + 1, colNames = FALSE)

# Save the updated workbook
saveWorkbook(wb, "Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx", overwrite = TRUE)

# Print the cutoff values for verification
print(cutoff_df)
```


##Decile Regression 3


Log+1 total FDI on log+1 total passengers flying in, with country fixed effects.
```{r C_quantile}
qr.model <- rq(log_FDI_n ~ ln_pass + factor(Country.Name), 
               data = data2, tau = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1))

qr.model[["coefficients"]]
```

```{r C_extract_coefficients_significance}
# Extract the summary from the quantile regression model
summary_output <- summary(qr.model, se = "boot")

# Extract the coefficients with significance stars
coefficients_with_stars <- extract_coefficients(summary_output)

# Print the coefficients with stars to check
print(coefficients_with_stars)

# Define the coefficient names and tau levels
coef_names <- c("Intercept", "ln_pass")  # Only relevant coefficients
tau_levels <- seq(0.1, 1, by = 0.1)

# Create a data frame to hold tau levels and variable names
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)
coef_with_tau <- coef_with_tau %>% arrange(as.numeric(tau))

# Filter out the country fixed effects (keeping only Intercept and ln_pass)
num_tau_levels <- length(tau_levels)
num_coefficients <- length(coef_names)
coefficients_filtered <- coefficients_with_stars[1:(num_tau_levels * num_coefficients)]

# Combine the filtered coefficients with the tau information
coef_with_tau$coefficients <- coefficients_filtered

# Print to verify
print(coef_with_tau)
```

```{r C_export-to-excel}
# Create a data frame to store the formula and weights information
additional_info <- data.frame(
  tau = NA,
  variable = NA,
  coefficients = NA
)

# Add the formula information
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Formula", coefficients = as.character(qr.model$formula)))

# Add the weights information
weights <- ifelse(is.null(qr.model$call$weights), "N/A", as.character(qr.model$call$weights))
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Weights", coefficients = weights))

# Combine the coefficients data frame (without fixed effects) with the additional information
final_df <- rbind(coef_with_tau, additional_info)

# Load the existing Excel file
wb <- loadWorkbook("Decile Analysis/Coefficient Tables/exported_tables.xlsx")

# Get the names of existing sheets
sheet_names <- names(wb$worksheets)

# Read the data from the first sheet to determine the starting column
sheet_data <- read.xlsx("Decile Analysis/Coefficient Tables/exported_tables.xlsx", sheet = 1)
current_col <- max(1, ncol(sheet_data) + 1)

# Write the data (coefficients and additional info) to the existing Excel file
writeData(wb, sheet = 1, final_df, startCol = current_col, startRow = 1)

# Save the changes to the Excel file
saveWorkbook(wb, "Decile Analysis/Coefficient Tables/exported_tables.xlsx", overwrite = TRUE)

```

```{r C_plot_alltaus}
# Extract coefficients without stars from the summary output
coefficients_without_stars <- extract_coefficients_nostars(summary_output)

# Filter out the country fixed effects
num_tau_levels <- length(tau_levels)
num_coefficients <- length(coef_names)
coefficients_filtered <- coefficients_without_stars[1:(num_tau_levels * num_coefficients)]

# Create a dataframe with tau and variable combinations
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)

# Arrange by tau for plotting
coef_with_tau <- coef_with_tau %>%
  arrange(as.numeric(tau))

# Combine coefficients without stars and tau information (only for relevant variables)
coef_with_tau$coefficients <- coefficients_filtered

# Filter out intercept if you want to plot only the variable of interest
coef_with_tau <- coef_with_tau %>%
  filter(variable == "ln_pass")

# Load necessary libraries for plotting
library(ggplot2)

# Plot coefficients against tau
ggplot(coef_with_tau, aes(x = tau, y = as.numeric(coefficients), group = 1)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") + 
  labs(x = "Tau (Logged Total Passengers)", 
       y = "Coefficients (relationship with logged total nominal FDI in terms of $US)", 
       title = "Coefficients vs. Tau",
       subtitle = "With Country Fixed Effects") +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1))

# Save the plot as a .jpg file
ggsave("Decile Analysis/Plots/decile_plotC.jpg", width = 10, height = 5, units = "in", dpi = 300)

```

```{r C_cutoffs}
# Calculate the quantiles for logged total passengers
passenger_cutoffs <- quantile(data2$ln_pass, probs = seq(0, 1, by = 0.1))

# Create a data frame for cutoffs
cutoff_df <- data.frame(
  Tau = seq(0, 1, by = 0.1),
  Cutoff = passenger_cutoffs
)

# Create a note for the model variables
model_note <- "Model: Logged total FDI on logged total passengers (ln_pass), with country fixed effects."

# Load necessary library for Excel export
library(openxlsx)

# Load the existing workbook for Tau cutoffs
wb <- loadWorkbook("Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx")

# Determine the next available row to insert data
existing_data <- read.xlsx("Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx", sheet = "Tau_Cutoffs")
start_row <- nrow(existing_data) + 3  # Two empty lines before data

# Write the cutoff data to the existing sheet with two empty lines before
writeData(wb, sheet = "Tau_Cutoffs", cutoff_df, startRow = start_row, colNames = TRUE)

# Write the model note at the next row
writeData(wb, sheet = "Tau_Cutoffs", model_note, startRow = start_row + nrow(cutoff_df) + 1, colNames = FALSE)

# Save the updated workbook
saveWorkbook(wb, "Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx", overwrite = TRUE)

# Print the cutoff values for verification
print(cutoff_df)
```



##Decile Regression 4
Decile OLS regression of total FDI on PERCENTAGE INCREASE of passengers flying into a country on US carriers CONTROLLED by GDP and battle fatalities

```{r D_quantile}
qr.model <- rq(log_FDI_n ~ passengers.in.change.pct + ln_battle_fatalities + log_GDP_r, 
               data = data2, tau = c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1))

qr.model[["coefficients"]]
```

```{r D_extract_coefficients_significance}
summary_output <- summary(qr.model, se = "boot")
coefficients_with_stars <- extract_coefficients(summary_output)
print(coefficients_with_stars)

# Extracted coefficients with tau and variable names
coef_names <- c("Intercept", "passengers.in.change.pct", "ln_battle_fatalities", "log_GDP_r")
tau_levels <- seq(0.1, 1, by = 0.1)
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)

coef_with_tau <- coef_with_tau %>%
  arrange(as.numeric(tau))

# Combine coefficients with stars and tau information
coef_with_tau$coefficients <- coefficients_with_stars 
```

```{r D_export-to-excel}
#install.packages("openxlsx")
#library(openxlsx)

# Create a data frame to store the formula and weights information
additional_info <- data.frame(
  tau = NA,
  variable = NA,
  coefficients = NA
)

# Add the formula information
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Formula", coefficients = as.character(qr.model$formula)))

# Add the weights information
weights <- ifelse(is.null(qr.model$call$weights), "N/A", as.character(qr.model$call$weights))
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Weights", coefficients = weights))

# Combine the coefficients data frame with the additional information data frame
final_df <- rbind(coef_with_tau, additional_info)

# Load the existing Excel file
wb <- loadWorkbook("Decile Analysis/Coefficient Tables/exported_tables.xlsx")

# Get the names of existing sheets
sheet_names <- names(wb$worksheets)

# Get the number of columns in the first sheet
sheet_data <- read.xlsx("Decile Analysis/Coefficient Tables/exported_tables.xlsx", sheet = 1)
current_col <- max(1, ncol(sheet_data) + 1)

# Write the data to the existing Excel file
writeData(wb, sheet = 1, final_df, startCol = current_col, startRow = 1)

# Save the changes to the Excel file
saveWorkbook(wb, "Decile Analysis/Coefficient Tables/exported_tables.xlsx", overwrite = TRUE)
```

```{r D_plot_alltaus}
coefficients_without_stars <- extract_coefficients_nostars(summary_output)

coef_names <- c("Intercept", "passengers.in.change.pct", "ln_battle_fatalities", "log_GDP_r")
tau_levels <- seq(0.1, 1, by = 0.1)
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)

coef_with_tau <- coef_with_tau %>%
  arrange(as.numeric(tau))

# Combine coefficients with stars and tau information
coef_with_tau$coefficients <- coefficients_without_stars 

coef_with_tau <- coef_with_tau %>%
  filter(variable != "Intercept", 
         variable != "ln_battle_fatalities",
         variable != "log_GDP_r")

# Plotting coefficients against tau
library(ggplot2)
ggplot(coef_with_tau, aes(x = tau, y = as.numeric(coefficients), group = 1)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") + 
  labs(x = "Tau (percent change in passengers flying into the country)", y = "Coefficients (relationship with logged total nominal FDI in terms of $US)", title = "Coefficients vs. Tau", subtitle = "Controlled by natural log of battle fatalities AND GDP") +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1))

ggsave("Decile Analysis/Plots/decile_plotD.jpg", width = 10, height = 5, units = "in", dpi = 300)
```

```{r D_cutoffs}
# Calculate the quantiles for logged total passengers
passenger_cutoffs <- quantile(data2$passengers.in.change.pct, probs = seq(0, 1, by = 0.1))

# Create a data frame for cutoffs
cutoff_df <- data.frame(
  Tau = seq(0, 1, by = 0.1),
  Cutoff = passenger_cutoffs
)

# Create a note for the model variables
model_note <- "Model: Logged total FDI on passengers in change pct, controlled by ln battle fatalities and log real GDP."

# Load necessary library for Excel export
library(openxlsx)

# Load the existing workbook for Tau cutoffs
wb <- loadWorkbook("Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx")

# Determine the next available row to insert data
existing_data <- read.xlsx("Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx", sheet = "Tau_Cutoffs")
start_row <- nrow(existing_data) + 3  # Two empty lines before data

# Write the cutoff data to the existing sheet with two empty lines before
writeData(wb, sheet = "Tau_Cutoffs", cutoff_df, startRow = start_row, colNames = TRUE)

# Write the model note at the next row
writeData(wb, sheet = "Tau_Cutoffs", model_note, startRow = start_row + nrow(cutoff_df) + 1, colNames = FALSE)

# Save the updated workbook
saveWorkbook(wb, "Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx", overwrite = TRUE)

# Print the cutoff values for verification
print(cutoff_df)
```



##Decile Regression 5 (same as 4 but with country fixed effects)

```{r E_quantile}
qr.model <- rq(log_FDI_n ~ passengers.in.change.pct + ln_battle_fatalities + log_GDP_r + factor(Country.Name), 
               data = data2, tau = c(0.1, 0.2, 0.3, 0.4, 0.5, 0.6, 0.7, 0.8, 0.9, 1))

qr.model[["coefficients"]]
```

```{r E_extract_coefficients_significance}
# Extract the summary from the quantile regression model
summary_output <- summary(qr.model, se = "boot")

# Extract the coefficients with significance stars
coefficients_with_stars <- extract_coefficients(summary_output)

# Print the coefficients with stars to check
print(coefficients_with_stars)

# Define the coefficient names and tau levels
coef_names <- c("Intercept", "passengers.in.change.pct")  # Only relevant coefficients
tau_levels <- seq(0.1, 1, by = 0.1)

# Create a data frame to hold tau levels and variable names
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)
coef_with_tau <- coef_with_tau %>% arrange(as.numeric(tau))

# Filter out the country fixed effects (keeping only Intercept and ln_pass)
num_tau_levels <- length(tau_levels)
num_coefficients <- length(coef_names)
coefficients_filtered <- coefficients_with_stars[1:(num_tau_levels * num_coefficients)]

# Combine the filtered coefficients with the tau information
coef_with_tau$coefficients <- coefficients_filtered

# Print to verify
print(coef_with_tau)
```

```{r E_export-to-excel}
# Create a data frame to store the formula and weights information
additional_info <- data.frame(
  tau = NA,
  variable = NA,
  coefficients = NA
)

# Add the formula information
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Formula", coefficients = as.character(qr.model$formula)))

# Add the weights information
weights <- ifelse(is.null(qr.model$call$weights), "N/A", as.character(qr.model$call$weights))
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Weights", coefficients = weights))

# Combine the coefficients data frame (without fixed effects) with the additional information
final_df <- rbind(coef_with_tau, additional_info)

# Load the existing Excel file
wb <- loadWorkbook("Decile Analysis/Coefficient Tables/exported_tables.xlsx")

# Get the names of existing sheets
sheet_names <- names(wb$worksheets)

# Read the data from the first sheet to determine the starting column
sheet_data <- read.xlsx("Decile Analysis/Coefficient Tables/exported_tables.xlsx", sheet = 1)
current_col <- max(1, ncol(sheet_data) + 1)

# Write the data (coefficients and additional info) to the existing Excel file
writeData(wb, sheet = 1, final_df, startCol = current_col, startRow = 1)

# Save the changes to the Excel file
saveWorkbook(wb, "Decile Analysis/Coefficient Tables/exported_tables.xlsx", overwrite = TRUE)

```

```{r E_plot_alltaus}
# Extract coefficients without stars from the summary output
coefficients_without_stars <- extract_coefficients_nostars(summary_output)

# Filter out the country fixed effects
num_tau_levels <- length(tau_levels)
num_coefficients <- length(coef_names)
coefficients_filtered <- coefficients_without_stars[1:(num_tau_levels * num_coefficients)]

# Create a dataframe with tau and variable combinations
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)

# Arrange by tau for plotting
coef_with_tau <- coef_with_tau %>%
  arrange(as.numeric(tau))

# Combine coefficients without stars and tau information (only for relevant variables)
coef_with_tau$coefficients <- coefficients_filtered

# Filter out intercept if you want to plot only the variable of interest
coef_with_tau <- coef_with_tau %>%
  filter(variable == "passengers.in.change.pct")

# Load necessary libraries for plotting
library(ggplot2)

# Plot coefficients against tau
ggplot(coef_with_tau, aes(x = tau, y = as.numeric(coefficients), group = 1)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") + 
  labs(x = "Tau (change in passengers pct)", 
       y = "Coefficients (relationship with logged total nominal FDI in terms of $US)", 
       title = "Coefficients vs. Tau",
       subtitle = "With controls (battle fatalities and Real GDP) and country fixed effects") +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1))

# Save the plot as a .jpg file
ggsave("Decile Analysis/Plots/decile_plotE.jpg", width = 10, height = 5, units = "in", dpi = 300)

```

```{r E_cutoffs}
# Calculate the quantiles for logged total passengers
passenger_cutoffs <- quantile(data2$passengers.in.change.pct, probs = seq(0, 1, by = 0.1))

# Create a data frame for cutoffs
cutoff_df <- data.frame(
  Tau = seq(0, 1, by = 0.1),
  Cutoff = passenger_cutoffs
)

# Create a note for the model variables
model_note <- "Model: Logged total FDI on passengers in change pct, with same controls as above AND country fixed effects."

# Load necessary library for Excel export
library(openxlsx)

# Load the existing workbook for Tau cutoffs
wb <- loadWorkbook("Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx")

# Determine the next available row to insert data
existing_data <- read.xlsx("Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx", sheet = "Tau_Cutoffs")
start_row <- nrow(existing_data) + 3  # Two empty lines before data

# Write the cutoff data to the existing sheet with two empty lines before
writeData(wb, sheet = "Tau_Cutoffs", cutoff_df, startRow = start_row, colNames = TRUE)

# Write the model note at the next row
writeData(wb, sheet = "Tau_Cutoffs", model_note, startRow = start_row + nrow(cutoff_df) + 1, colNames = FALSE)

# Save the updated workbook
saveWorkbook(wb, "Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx", overwrite = TRUE)

# Print the cutoff values for verification
print(cutoff_df)
```



##Decile Regression 6
Decile OLS regression of total FDI on PERCENTAGE INCREASE of passengers flying into a country on US carriers.

```{r F_quantile}
qr.model <- rq(log_FDI_n ~ passengers.in.change.pct, 
               data = data2, tau = c(0.1,0.2,0.3,0.4,0.5,0.6,0.7,0.8,0.9,1))

qr.model[["coefficients"]]
```

```{r F_extract_coefficients_significance}
summary_output <- summary(qr.model, se = "boot")
coefficients_with_stars <- extract_coefficients(summary_output)
print(coefficients_with_stars)

# Extracted coefficients with tau and variable names
coef_names <- c("Intercept", "passengers.in.change.pct")
tau_levels <- seq(0.1, 1, by = 0.1)
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)

coef_with_tau <- coef_with_tau %>%
  arrange(as.numeric(tau))

# Combine coefficients with stars and tau information
coef_with_tau$coefficients <- coefficients_with_stars 
```

```{r F_export-to-excel}
#install.packages("openxlsx")
#library(openxlsx)

# Create a data frame to store the formula and weights information
additional_info <- data.frame(
  tau = NA,
  variable = NA,
  coefficients = NA
)

# Add the formula information
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Formula", coefficients = as.character(qr.model$formula)))

# Add the weights information
weights <- ifelse(is.null(qr.model$call$weights), "N/A", as.character(qr.model$call$weights))
additional_info <- rbind(additional_info, data.frame(tau = NA, variable = "Weights", coefficients = weights))

# Combine the coefficients data frame with the additional information data frame
final_df <- rbind(coef_with_tau, additional_info)

# Load the existing Excel file
wb <- loadWorkbook("Decile Analysis/Coefficient Tables/exported_tables.xlsx")

# Get the names of existing sheets
sheet_names <- names(wb$worksheets)

# Get the number of columns in the first sheet
sheet_data <- read.xlsx("Decile Analysis/Coefficient Tables/exported_tables.xlsx", sheet = 1)
current_col <- max(1, ncol(sheet_data) + 1)

# Write the data to the existing Excel file
writeData(wb, sheet = 1, final_df, startCol = current_col, startRow = 1)

# Save the changes to the Excel file
saveWorkbook(wb, "Decile Analysis/Coefficient Tables/exported_tables.xlsx", overwrite = TRUE)
```

```{r F_plot_alltaus}
coefficients_without_stars <- extract_coefficients_nostars(summary_output)

coef_names <- c("Intercept", "passengers.in.change.pct")
tau_levels <- seq(0.1, 1, by = 0.1)
coef_with_tau <- expand.grid(tau = tau_levels, variable = coef_names)

coef_with_tau <- coef_with_tau %>%
  arrange(as.numeric(tau))

# Combine coefficients with stars and tau information
coef_with_tau$coefficients <- coefficients_without_stars 

coef_with_tau <- coef_with_tau %>%
  filter(variable != "Intercept")

# Plotting coefficients against tau
library(ggplot2)
ggplot(coef_with_tau, aes(x = tau, y = as.numeric(coefficients), group = 1)) +
  geom_point() +
  geom_line() +
  geom_hline(yintercept = 0, linetype = "dashed", color = "red") + 
  labs(x = "Tau (percent change in passengers flying into the country)", y = "Coefficients (relationship with logged total nominal FDI in terms of $US)", title = "Coefficients vs. Tau") +
  scale_x_continuous(breaks = seq(0, 1, by = 0.1))

ggsave("Decile Analysis/Plots/decile_plotF.jpg", width = 10, height = 5, units = "in", dpi = 300)
```

```{r F_cutoffs}
# Calculate the quantiles for logged total passengers
passenger_cutoffs <- quantile(data2$passengers.in.change.pct, probs = seq(0, 1, by = 0.1))

# Create a data frame for cutoffs
cutoff_df <- data.frame(
  Tau = seq(0, 1, by = 0.1),
  Cutoff = passenger_cutoffs
)

# Create a note for the model variables
model_note <- "Model: Logged total FDI on passengers in change pct."

# Load necessary library for Excel export
library(openxlsx)

# Load the existing workbook for Tau cutoffs
wb <- loadWorkbook("Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx")

# Determine the next available row to insert data
existing_data <- read.xlsx("Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx", sheet = "Tau_Cutoffs")
start_row <- nrow(existing_data) + 3  # Two empty lines before data

# Write the cutoff data to the existing sheet with two empty lines before
writeData(wb, sheet = "Tau_Cutoffs", cutoff_df, startRow = start_row, colNames = TRUE)

# Write the model note at the next row
writeData(wb, sheet = "Tau_Cutoffs", model_note, startRow = start_row + nrow(cutoff_df) + 1, colNames = FALSE)

# Save the updated workbook
saveWorkbook(wb, "Decile Analysis/Coefficient Tables/tau_cutoffs.xlsx", overwrite = TRUE)

# Print the cutoff values for verification
print(cutoff_df)
```

