---
title: "Difference-in-Difference Analysis"
author: "Michelle Schultze"
date: "Sept 21, 2024"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---
---

```{r}
library(tidyverse)
library(dplyr)
library(readr)
library(readxl)
library(naniar)
library("readr")
library("microsynth")
library("LowRankQP")
#install.packages("quantreg")
library(quantreg)
#install.packages("openxlsx")
library(openxlsx)
library(lmtest)
library(modelsummary)
library(kableExtra)

setwd('/Users/michelle/Documents/ukr2024/Replication files')
data <- read_csv("full_data.csv")
```

Generate treatment variable (coded as “1” for any year after the largest percentage increase in a country's air traffic, given that the amount exceeds a 200% increase, or a tripling), and the post*treatment variable (the number of years after the first treatment year).

```{r}
dataDID <- data %>%
  group_by(Country.Name) %>%
  mutate(flag = ifelse((passengers.in.change.pct >= 200 & passengers.in.change.pct == max(passengers.in.change.pct)), TRUE, FALSE))

dataDID <- dataDID %>%
  arrange(Country.Name, year) %>%
  group_by(Country.Name) %>%
  mutate(flag = ifelse((((Country.Name == lag(Country.Name)) & (lag(flag) == TRUE)) | flag == TRUE), TRUE, flag)) %>%
  mutate(flag = ifelse(cumsum(flag) > 0, TRUE, FALSE))

dataDID <- dataDID %>%
  mutate(flag = ifelse(is.na(flag), 0, flag)) %>%
  mutate(Treat = as.integer(flag)) %>%
  group_by(Country.Name) %>%
  mutate(After = cumsum(flag)) %>%
  mutate(TreatAfter = Treat * After,
         BattleAfter = lag(log_battle, default = 0) * After,
         BattleTreat = lag(log_battle, default = 0) * Treat)


#lm(ln_FDI ~ Treat + After + TreatAfter + ln_battle_fatalities * Treat + ln_GDP)

dataDID %>%
  group_by(Country.Name, After) %>%
  filter(After == 1) %>%
  summarize(n = n()) #27 countries in the sample where this occurs
```

#Regular model

```{r}
models <- NA
models <- list()
hsd_testing <- NA
hsd_testing <- list()

model.1a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct, data = dataDID)
models[["IHS-Transformed Real FDI"]][["1a"]] <- model.1a
hsd_testing[["IHS-Transformed Real FDI"]][["1a"]] <- bptest(model.1a)

model.2a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle), data = dataDID)
models[["IHS-Transformed Real FDI"]][["2a"]] <- model.2a
hsd_testing[["IHS-Transformed Real FDI"]][["2a"]] <- bptest(model.2a)

model.3a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r), data = dataDID)
models[["IHS-Transformed Real FDI"]][["3a"]] <- model.3a
hsd_testing[["IHS-Transformed Real FDI"]][["3a"]] <- bptest(model.3a)

model.4a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + lag(GDP.growth.annual.pct), data = dataDID)
models[["IHS-Transformed Real FDI"]][["4a"]] <- model.4a
hsd_testing[["IHS-Transformed Real FDI"]][["4a"]] <- bptest(model.4a)

model.5a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + BattleTreat, data = dataDID)
models[["IHS-Transformed Real FDI"]][["5a"]] <- model.5a
hsd_testing[["IHS-Transformed Real FDI"]][["5a"]] <- bptest(model.5a)

model.6a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + BattleAfter, data = dataDID)
models[["IHS-Transformed Real FDI"]][["6a"]] <- model.6a
hsd_testing[["IHS-Transformed Real FDI"]][["6a"]] <- bptest(model.6a)

model.7a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + factor(Country.Name), data = dataDID)
models[["IHS-Transformed Real FDI"]][["7a"]] <- model.7a
hsd_testing[["IHS-Transformed Real FDI"]][["7a"]] <- bptest(model.7a)

model.8a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + lag(GDP.growth.annual.pct) + factor(Country.Name), data = dataDID)
models[["IHS-Transformed Real FDI"]][["8a"]] <- model.8a
hsd_testing[["IHS-Transformed Real FDI"]][["8a"]] <- bptest(model.8a)

model.9a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + BattleTreat + factor(Country.Name), data = dataDID)
models[["IHS-Transformed Real FDI"]][["9a"]] <- model.9a
hsd_testing[["IHS-Transformed Real FDI"]][["9a"]] <- bptest(model.9a)

model.10a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + BattleAfter + factor(Country.Name), data = dataDID)
models[["IHS-Transformed Real FDI"]][["10a"]] <- model.10a
hsd_testing[["IHS-Transformed Real FDI"]][["10a"]] <- bptest(model.10a)
```

```{r}
models_unlisted <- unlist(models, recursive=FALSE)
names(models_unlisted) <- c('1a', '2a', '3a', '4a', '5a', '6a', '3a, FE', '4a, FE', '5a, FE', '6a, FE')

cm <- c( '(Intercept)' = 'Constant', 
         'Treat' = 'Treatment',
         'After' = 'Post-Treatment',
         'TreatAfter' = 'Treat * Post',
         'passengers.in.change.pct' = 'Change in passengers (%)',
         'lag(log_battle)' = 'Battle fatalities (log)', 
         'lag(log_GDP_r)' = 'Real GDP (int$, log, lag)',
         'lag(GDP.growth.annual.pct)' = 'GDP Growth (%, lag)',
         'BattleTreat' = 'Battle * Treatment',
         'BattleAfter' = 'Battle * Post-Treatment')

# Generate the model summary
output <- msummary(
  models_unlisted, output = 'kableExtra', coef_map = cm, stars = TRUE, 
  gof_omit = 'IC|Log|Adj', title = "IHS-Transfomed Real FDI", 
  statistic = 'p.value', conf_level = 0.95, vcov = 'robust'
)

output <- output %>%
  kableExtra::footnote(general = "The last four models include country fixed effects.")

# Save the table as an HTML file
save_kable(output, file = "DID_Summary.html")
```

#Scaling passengers 

Interpretation is hard here because the coefficients on percent change in passengers will be too small for interpretation (representing each 1% increase in passengers). Let's divide passengers/100 so that we have them in fractional terms. The coefficient will describe every additional 100% increase in passengers (where -50% is a decrease by half of the previous value, 0% there is no change, 100% is a doubling, and 200% is a tripling)
```{r}
dataDID <- dataDID %>%
  mutate(passengers.in.change.pct = passengers.in.change.pct / 100)
```

```{r}
models <- NA
models <- list()
hsd_testing <- NA
hsd_testing <- list()

model.1a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct, data = dataDID)
models[["IHS-Transformed Real FDI"]][["1a"]] <- model.1a
hsd_testing[["IHS-Transformed Real FDI"]][["1a"]] <- bptest(model.1a)

model.2a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle), data = dataDID)
models[["IHS-Transformed Real FDI"]][["2a"]] <- model.2a
hsd_testing[["IHS-Transformed Real FDI"]][["2a"]] <- bptest(model.2a)

model.3a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r), data = dataDID)
models[["IHS-Transformed Real FDI"]][["3a"]] <- model.3a
hsd_testing[["IHS-Transformed Real FDI"]][["3a"]] <- bptest(model.3a)

model.4a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + lag(GDP.growth.annual.pct), data = dataDID)
models[["IHS-Transformed Real FDI"]][["4a"]] <- model.4a
hsd_testing[["IHS-Transformed Real FDI"]][["4a"]] <- bptest(model.4a)

model.5a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + BattleTreat, data = dataDID)
models[["IHS-Transformed Real FDI"]][["5a"]] <- model.5a
hsd_testing[["IHS-Transformed Real FDI"]][["5a"]] <- bptest(model.5a)

model.6a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + BattleAfter, data = dataDID)
models[["IHS-Transformed Real FDI"]][["6a"]] <- model.6a
hsd_testing[["IHS-Transformed Real FDI"]][["6a"]] <- bptest(model.6a)

model.7a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + factor(Country.Name), data = dataDID)
models[["IHS-Transformed Real FDI"]][["7a"]] <- model.7a
hsd_testing[["IHS-Transformed Real FDI"]][["7a"]] <- bptest(model.7a)

model.8a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + lag(GDP.growth.annual.pct) + factor(Country.Name), data = dataDID)
models[["IHS-Transformed Real FDI"]][["8a"]] <- model.8a
hsd_testing[["IHS-Transformed Real FDI"]][["8a"]] <- bptest(model.8a)

model.9a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + BattleTreat + factor(Country.Name), data = dataDID)
models[["IHS-Transformed Real FDI"]][["9a"]] <- model.9a
hsd_testing[["IHS-Transformed Real FDI"]][["9a"]] <- bptest(model.9a)

model.10a <- lm(ihs_FDI_r ~ Treat + After + TreatAfter + passengers.in.change.pct + lag(log_battle) + lag(log_GDP_r) + BattleAfter + factor(Country.Name), data = dataDID)
models[["IHS-Transformed Real FDI"]][["10a"]] <- model.10a
hsd_testing[["IHS-Transformed Real FDI"]][["10a"]] <- bptest(model.10a)
```

```{r}
models_unlisted <- unlist(models, recursive=FALSE)
names(models_unlisted) <- c('1a', '2a', '3a', '4a', '5a', '6a', '3a, FE', '4a, FE', '5a, FE', '6a, FE')

cm <- c( '(Intercept)' = 'Constant', 
         'Treat' = 'Treatment',
         'After' = 'Post-Treatment',
         'TreatAfter' = 'Treat * Post',
         'passengers.in.change.pct' = 'Change in passengers (%)',
         'lag(log_battle)' = 'Battle fatalities (log)', 
         'lag(log_GDP_r)' = 'Real GDP (int$, log, lag)',
         'lag(GDP.growth.annual.pct)' = 'GDP Growth (%, lag)',
         'BattleTreat' = 'Battle * Treatment',
         'BattleAfter' = 'Battle * Post-Treatment')

# Generate the model summary
output <- msummary(
  models_unlisted, output = 'kableExtra', coef_map = cm, stars = TRUE, 
  gof_omit = 'IC|Log|Adj', title = "IHS-Transfomed Real FDI", 
  statistic = 'p.value', conf_level = 0.95, vcov = 'robust'
)

output <- output %>%
  kableExtra::footnote(general = "The last four models include country fixed effects.")

# Save the table as an HTML file
save_kable(output, file = "DID_Summary_scaled.html")
```

