---
title: "Generalized Synthetic Control"
author: "Michelle Schultze"
date: "Oct 20, 2024"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
    toc_float: yes
---
---

```{r}
#install.packages("urca")
library(urca)
library(dplyr)
#install.packages("knitr")
library(knitr)
library(readr)
library(Synth)
#install.packages("microsynth", repos = "http://cran.us.r-project.org")
#install.packages("LowRankQP", repos = "http://cran.us.r-project.org")
#install.packages("tidyverse", repos = "http://cran.us.r-project.org")
library("tidyverse")
library("microsynth")
library("LowRankQP")

setwd('/Users/michelle/Documents/ukr2024/Replication files')
data <- read_csv("full_data_1990.csv")
```
I went back into the data file, keeping data ≥1990 and adding more variables.

Treatment is TRUE if the country experienced a long-term (≥2y) closure of its 
main airport and a discrete and sustained reopening of the airport. This may be 
as a result of war or (more rarely, and only in the case of Haiti) a 
natural disaster.
```{r}
# Define the treatment years for each country
treatment_years <- data.frame(
  Country.Name = c("Bosnia and Herzegovina", "Kosovo", "Timor Leste", "Haiti", 
                   "Iraq", "Afghanistan", "Liberia", "Somalia"),
  Treatment.Year = c(1996, 1999, 2000, 2012, 2003, 2002, 2003, 2010)
)

# Merge the treatment years into your original dataset
data2 <- data %>%
  left_join(treatment_years, by = "Country.Name")

# Create Treatment and Post-Treatment columns
data2 <- data2 %>%
  mutate(
    Treatment = ifelse(year >= as.numeric(Treatment.Year) & !is.na(Treatment.Year), 1, 0),
    Post_Treatment = ifelse(year > as.numeric(Treatment.Year) & !is.na(Treatment.Year), 1, 0)
  )

#Only a few countries have enough data for this to work. we have to drop the ones that don't have pre-treatment years.
# Keep all years for countries that have pre-treatment data or no treatment year
valid_countries <- data2 %>%
  group_by(Country.Name) %>%
  filter(any(year < Treatment.Year) | is.na(Treatment.Year)) %>%
  pull(Country.Name) %>%  # Extract valid country names
  unique()

# Filter the original data to keep only valid countries
data2 <- data2 %>%
  filter(Country.Name %in% valid_countries) %>%
  filter(Country.Name != "Somalia")
```

Though we found 8 examples of this occurring 1990-2019, only 3 of them end up 
making it into the SCM because we lack enough data to describe a pre-treatment 
environment for Afghanistan, Timor Leste, Bosnia and Herzegovina, Kosovo, and 
Somalia. But we did retain Haiti, Liberia, and Iraq. Such a lack of data is to 
be expected: such detailed data is rare to be collected in war-afflicted 
countries, especially before 2015.

Handling NAs:
```{r}
# Drop specific variables with NAs from the dataset (they're unimportant anyway)
data2 <- data2 %>%
  select(-c(log_FDI_n, log_FDI_r, Inflation.GDP.deflator.annual.pct, `GDP deflator (base year varies by country)`, Treatment.Year))

data2_cleaned <- na.omit(data2)

missing_years <- data2_cleaned %>%
  group_by(Country.Name) %>%
  summarise(min_year = min(year), max_year = max(year), n_years = n()) %>%
  filter(n_years != (max_year - min_year + 1))

#El Salvador missing 1995

# Create a function to detect missing years for each country
missing_years_details <- function(data) {
  data %>%
    group_by(Country.Name) %>%
    summarise(
      all_years = list(min(year):max(year)),  # Generate the full sequence of years
      present_years = list(year),             # List of years present in the data
      missing_years = list(setdiff(all_years[[1]], present_years[[1]]))  # Find missing years
    ) %>%
    filter(lengths(missing_years) > 0)  # Keep only countries with missing years
}

# Apply the function to your cleaned dataset
missing_years_info <- missing_years_details(data2_cleaned)
```

#aDID

##total FDI n

```{r}
# Load necessary libraries
library(dplyr)
library(fixest) # For regression with fixed effects
library(ggplot2)  # For visualization

#c("GDP.current.US$", "total_FDI_n")

# Estimate the Augmented DID Model with Country and Time Fixed Effects
model <- feols(
  total_FDI_n ~ Treatment * Post_Treatment + log(GDP_USD) + log(fatalities.y.Battles) | Country.Name + year,
  data = data2
)

# Summary of the model
summary(model)
```

```{r}
# Load necessary libraries
#library(fixest)   # For running fixed-effects models
#library(ggplot2)  # For visualization
#library(dplyr)    # For data wrangling

# Prepare the dataset: Create Treatment.Year if not already present
data2 <- data2 %>%
  group_by(Country.Name) %>%
  mutate(Treatment.Year = ifelse(Treatment == 1, min(year[Treatment == 1]), NA)) %>%
  fill(Treatment.Year, .direction = "downup") %>%
  ungroup()

# Predicted values from the model for plotting
data2 <- data2 %>%
  mutate(predicted = predict(model, newdata = data2))

# Create a DID Visualization
ggplot(data2, aes(x = year, y = predicted, color = Country.Name, group = Country.Name)) +
  geom_line(size = 1) +
  geom_vline(aes(xintercept = Treatment.Year), linetype = "dashed", color = "red") + 
  geom_text(data = data2 %>% filter(Country.Name %in% c("Haiti", "Liberia", "Iraq") & year == max(year)), 
            aes(label = Country.Name), 
            hjust = 1, vjust = 0, size = 4, color = "black") +  # Adjust the size of the labels
  labs(
    title = "Augmented DID: Treatment Effects across Haiti, Iraq, and Liberia",
    x = "Year", y = "Predicted Nominal FDI",
    caption = "Dashed lines indicate treatment years for each country."
  ) +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("augmented_did_plotA.png", width = 8, height = 6, dpi = 300)
```

##total FDI r

```{r}
# Load necessary libraries
library(dplyr)
library(fixest) # For regression with fixed effects
library(ggplot2)  # For visualization

#c("GDP.current.US$", "total_FDI_n")

# Estimate the Augmented DID Model with Country and Time Fixed Effects
model <- feols(
  total_FDI_r ~ Treatment * Post_Treatment | Country.Name + year,
  data = data2
)

# Summary of the model
summary(model)
```

```{r}
# Load necessary libraries
#library(fixest)   # For running fixed-effects models
#library(ggplot2)  # For visualization
#library(dplyr)    # For data wrangling

# Prepare the dataset: Create Treatment.Year if not already present
data2 <- data2 %>%
  group_by(Country.Name) %>%
  mutate(Treatment.Year = ifelse(Treatment == 1, min(year[Treatment == 1]), NA)) %>%
  fill(Treatment.Year, .direction = "downup") %>%
  ungroup()

# Predicted values from the model for plotting
data2 <- data2 %>%
  mutate(predicted = predict(model, newdata = data2))

# Create a DID Visualization
ggplot(data2, aes(x = year, y = predicted, color = Country.Name, group = Country.Name)) +
  geom_line(size = 1) +
  geom_vline(aes(xintercept = Treatment.Year), linetype = "dashed", color = "red") + 
  geom_text(data = data2 %>% filter(Country.Name %in% c("Haiti", "Liberia", "Iraq") & year == max(year)), 
            aes(label = Country.Name), 
            hjust = 1, vjust = 0, size = 4, color = "black") +  # Adjust the size of the labels
  labs(
    title = "Augmented DID: Treatment Effects across Haiti, Iraq, and Liberia",
    x = "Year", y = "Predicted Real FDI",
    caption = "Dashed lines indicate treatment years for each country."
  ) +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("augmented_did_plot_B.png", width = 8, height = 6, dpi = 300)
```


##Nominal GDP

```{r}
# Load necessary libraries
library(dplyr)
library(fixest) # For regression with fixed effects
library(ggplot2)  # For visualization

#c("GDP.current.US$", "total_FDI_n")

data2 <- data2 %>%
  rename(GDP_USD = `GDP.current.US$`)

# Estimate the Augmented DID Model with Country and Time Fixed Effects
model <- feols(
  GDP_USD ~ Treatment * Post_Treatment | Country.Name + year,
  data = data2
)

# Summary of the model
summary(model)
```

```{r}
# Load necessary libraries
#library(fixest)   # For running fixed-effects models
#library(ggplot2)  # For visualization
#library(dplyr)    # For data wrangling

# Prepare the dataset: Create Treatment.Year if not already present
data2 <- data2 %>%
  group_by(Country.Name) %>%
  mutate(Treatment.Year = ifelse(Treatment == 1, min(year[Treatment == 1]), NA)) %>%
  fill(Treatment.Year, .direction = "downup") %>%
  ungroup()

# Predicted values from the model for plotting
data2 <- data2 %>%
  mutate(predicted = predict(model, newdata = data2))

# Create a DID Visualization
ggplot(data2, aes(x = year, y = predicted, color = Country.Name, group = Country.Name)) +
  geom_line(size = 1) +
  geom_vline(aes(xintercept = Treatment.Year), linetype = "dashed", color = "red") + 
  geom_text(data = data2 %>% filter(Country.Name %in% c("Haiti", "Liberia", "Iraq") & year == max(year)), 
            aes(label = Country.Name), 
            hjust = 1, vjust = 0, size = 4, color = "black") +  # Adjust the size of the labels
  labs(
    title = "Augmented DID: Treatment Effects across Haiti, Iraq, and Liberia",
    x = "Year", y = "Predicted Nominal GDP",
    caption = "Dashed lines indicate treatment years for each country."
  ) +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("augmented_did_plot_C.png", width = 8, height = 6, dpi = 300)
```


# Battle fatalities covariate


##total FDI n

```{r}
# Load necessary libraries
library(dplyr)
library(fixest) # For regression with fixed effects
library(ggplot2)  # For visualization

#c("GDP.current.US$", "total_FDI_n")

# Estimate the Augmented DID Model with Country and Time Fixed Effects
model <- feols(
  total_FDI_n ~ Treatment * Post_Treatment + fatalities.y.Battles | Country.Name + year,
  data = data2
)

# Summary of the model
summary(model)
```

```{r}
# Load necessary libraries
#library(fixest)   # For running fixed-effects models
#library(ggplot2)  # For visualization
#library(dplyr)    # For data wrangling

# Prepare the dataset: Create Treatment.Year if not already present
data2 <- data2 %>%
  group_by(Country.Name) %>%
  mutate(Treatment.Year = ifelse(Treatment == 1, min(year[Treatment == 1]), NA)) %>%
  fill(Treatment.Year, .direction = "downup") %>%
  ungroup()

# Predicted values from the model for plotting
data2 <- data2 %>%
  mutate(predicted = predict(model, newdata = data2))

# Create a DID Visualization
ggplot(data2, aes(x = year, y = predicted, color = Country.Name, group = Country.Name)) +
  geom_line(size = 1) +
  geom_vline(aes(xintercept = Treatment.Year), linetype = "dashed", color = "red") + 
  geom_text(data = data2 %>% filter(Country.Name %in% c("Haiti", "Liberia", "Iraq") & year == max(year)), 
            aes(label = Country.Name), 
            hjust = 1, vjust = 0, size = 4, color = "black") +  # Adjust the size of the labels
  labs(
    title = "Augmented DID: Treatment Effects across Haiti, Iraq, and Liberia",
    subtitle = "with battle fatalities covariate",
    x = "Year", y = "Predicted Nominal FDI",
    caption = "Dashed lines indicate treatment years for each country."
  ) +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("augmented_did_plotA_BF.png", width = 8, height = 6, dpi = 300)
```

##total FDI r

```{r}
# Load necessary libraries
library(dplyr)
library(fixest) # For regression with fixed effects
library(ggplot2)  # For visualization

#c("GDP.current.US$", "total_FDI_n")

# Estimate the Augmented DID Model with Country and Time Fixed Effects
model <- feols(
  total_FDI_r ~ Treatment * Post_Treatment + fatalities.y.Battles | Country.Name + year,
  data = data2
)

# Summary of the model
summary(model)
```

```{r}
# Load necessary libraries
#library(fixest)   # For running fixed-effects models
#library(ggplot2)  # For visualization
#library(dplyr)    # For data wrangling

# Prepare the dataset: Create Treatment.Year if not already present
data2 <- data2 %>%
  group_by(Country.Name) %>%
  mutate(Treatment.Year = ifelse(Treatment == 1, min(year[Treatment == 1]), NA)) %>%
  fill(Treatment.Year, .direction = "downup") %>%
  ungroup()

# Predicted values from the model for plotting
data2 <- data2 %>%
  mutate(predicted = predict(model, newdata = data2))

# Create a DID Visualization
ggplot(data2, aes(x = year, y = predicted, color = Country.Name, group = Country.Name)) +
  geom_line(size = 1) +
  geom_vline(aes(xintercept = Treatment.Year), linetype = "dashed", color = "red") + 
  geom_text(data = data2 %>% filter(Country.Name %in% c("Haiti", "Liberia", "Iraq") & year == max(year)), 
            aes(label = Country.Name), 
            hjust = 1, vjust = 0, size = 4, color = "black") +  # Adjust the size of the labels
  labs(
    title = "Augmented DID: Treatment Effects across Haiti, Iraq, and Liberia",
    subtitle = "with battle fatalities covariate",
    x = "Year", y = "Predicted Real FDI",
    caption = "Dashed lines indicate treatment years for each country."
  ) +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("augmented_did_plot_B_BF.png", width = 8, height = 6, dpi = 300)
```


##Nominal GDP

```{r}
# Load necessary libraries
library(dplyr)
library(fixest) # For regression with fixed effects
library(ggplot2)  # For visualization

#c("GDP.current.US$", "total_FDI_n")

data2 <- data2 %>%
  rename(GDP_USD = `GDP.current.US$`)

# Estimate the Augmented DID Model with Country and Time Fixed Effects
model <- feols(
  GDP_USD ~ Treatment * Post_Treatment + fatalities.y.Battles | Country.Name + year,
  data = data2
)

# Summary of the model
summary(model)
```

```{r}
# Load necessary libraries
#library(fixest)   # For running fixed-effects models
#library(ggplot2)  # For visualization
#library(dplyr)    # For data wrangling

# Prepare the dataset: Create Treatment.Year if not already present
data2 <- data2 %>%
  group_by(Country.Name) %>%
  mutate(Treatment.Year = ifelse(Treatment == 1, min(year[Treatment == 1]), NA)) %>%
  fill(Treatment.Year, .direction = "downup") %>%
  ungroup()

# Predicted values from the model for plotting
data2 <- data2 %>%
  mutate(predicted = predict(model, newdata = data2))

# Create a DID Visualization
ggplot(data2, aes(x = year, y = predicted, color = Country.Name, group = Country.Name)) +
  geom_line(size = 1) +
  geom_vline(aes(xintercept = Treatment.Year), linetype = "dashed", color = "red") + 
  geom_text(data = data2 %>% filter(Country.Name %in% c("Haiti", "Liberia", "Iraq") & year == max(year)), 
            aes(label = Country.Name), 
            hjust = 1, vjust = 0, size = 4, color = "black") +  # Adjust the size of the labels
  labs(
    title = "Augmented DID: Treatment Effects across Haiti, Iraq, and Liberia",
    subtitle = "with battle fatalities covariate",
    x = "Year", y = "Predicted Nominal GDP",
    caption = "Dashed lines indicate treatment years for each country."
  ) +
  theme_minimal() +
  theme(legend.position = "none")

ggsave("augmented_did_plot_C_BF.png", width = 8, height = 6, dpi = 300)
```







## Liberia: Gsynth

```{r}
# Load necessary libraries
library(gsynth)
library(dplyr)
library(tidyr)

# Prepare your dataset
# Ensure your dataset is filtered for the relevant years (2003-2008) and only contains Liberia and control countries
data_filtered <- data2_cleaned %>%
  filter(year >= 2003 & year <= 2008) %>%
  filter(Country.Name == "Liberia" | Country.Name %in% c("Zimbabwe", "Mali", "Iran")) # Add relevant control countries

# Select only the relevant columns for reshaping
data_filtered <- data_filtered %>%
  select(Country.Name, year, Treatment, Post_Treatment, everything()) # Select all other columns

# Reshape the data to long format suitable for gsynth
data_long <- data_filtered %>%
  pivot_longer(cols = -c(Country.Name, year, Treatment, Post_Treatment), 
               names_to = "Indicator", 
               values_to = "Value")

# Check the reshaped data
head(data_long)

```




## LIBERIA: Synth breaks

```{r}
library(Synth)
library(dplyr)

# Assuming your data is loaded into a data frame called data2_cleaned
data <- data2_cleaned

# Convert Country.Name to factor
data$Country.Name <- as.character(data$Country.Name)

# Specify the intervention year and the treated unit (Liberia)
intervention_year <- 2003
treated_country <- "Liberia"

# Filter the data for the relevant years (5 years before and 5 years after)
data_filtered <- data %>%
  filter(year >= (intervention_year - 5) & year <= (intervention_year + 5))

# Ensure the required columns are numeric
numeric_columns <- c("GDP.growth.annual.pct", "Foreign.direct.investment.net.inflows.pct.of.GDP", 
                     "total.flights.in", "total.passengers.out")

# Convert specified columns to numeric, handle warnings
data_filtered[numeric_columns] <- lapply(data_filtered[numeric_columns], function(x) {
  as.numeric(as.character(x))  # Ensure conversion from factor/character to numeric
})

# Prepare the data for the Synth package
# Specify the dependent variable (outcome variable you want to model, e.g., total.passengers.in)
outcome_var <- "total.passengers.in"  # Adjust this to your outcome of interest

# Set up the data for Synth
dataprep_out <- dataprep(
  foo = as.data.frame(data_filtered),
  predictors = numeric_columns,
  dependent = outcome_var,
  unit.variable = "Country.Name",  # Ensure this is a factor
  time.variable = "year",
  treatment.identifier = treated_country,
  controls.identifier = data_filtered$Country.Name[data_filtered$Country.Name != treated_country],
  time.predictors.prior = seq(intervention_year - 5, intervention_year - 1),  # 5 years prior
  time.optimize.ssr = seq(intervention_year - 5, intervention_year - 1),   # Optimize over the same years
  time.plot = seq(intervention_year - 5, intervention_year + 5)              # Plot the full range
)

# Run the synthetic control model
synth_out <- synth(dataprep_out)

# Extract results for visualization and analysis
synth_tables <- synth.tab(synth.res = synth_out, dataprep.res = dataprep_out)

# Create a plot to visualize the synthetic control results
path.plot(synth.res = synth_out, dataprep.res = dataprep_out,
          Ylab = "Total Passengers In", Xlab = "Year", 
          Main = "Synthetic Control for Airport Reopening in Liberia")

# Print the synthetic control results
print(synth_tables)

```









## IRAQ

Prepare the Data for Iraq's Synthetic Control Model
```{r}
# Define Iraq's intervention year and pre-treatment start
intervention_year <- 2003
pre_treatment_start <- intervention_year - 5
post_treatment_end <- intervention_year + 5

# Subset data: Keep only years from 5 years before the intervention onward
data_scm <- data2_cleaned %>%
  filter(year >= pre_treatment_start & year <= post_treatment_end)

# Separate Iraq's data and donor pool
iraq_data <- data_scm %>% filter(Country.Name == "Iraq")
iraq_country <- unique(iraq_data$Country.Name) # for later
donor_pool <- data_scm %>% 
  filter(!Country.Name %in% c("Iraq", "Liberia", "Haiti"))
```

Identify Donor Countries Based on Pre-treatment Trends
```{r}
library(dplyr)
library(tidyr)
library(scales)  # For standardization

# Key variables for conflict and economic metrics
key_conflict_vars <- c(
  "count.events.y.All.types.of.violent.conflict", 
  "count.events.y.Battles", 
  "count.events.y.Explosions/Remote.violence", 
  "fatalities.y.Battles", 
  "fatalities.y.Violence.against.civilians"
)

key_economic_vars <- c(
  "Agriculture.forestry.and.fishing.value.added.pct.of.GDP", 
  "Mineral.rents.pct.of.GDP", 
  "Services.value.added.pct.of.GDP", 
  "Merchandise.trade.pct.of.GDP", 
  "Foreign.direct.investment.net.inflows.pct.of.GDP"
)

# Define the weighting factors for conflict and economic metrics
conflict_weight <- 3
economic_weight <- 2 

# Pre-treatment period (5 years before intervention)
pre_treatment_years <- pre_treatment_start:(intervention_year - 1)

# Filter Iraq's data for all relevant years (not just pre-treatment)
iraq_data <- data_scm %>% 
  filter(Country.Name == "Iraq") %>% 
  summarise(across(all_of(c(key_conflict_vars, key_economic_vars)), mean, na.rm = TRUE))

# For donor countries, summarize over the relevant years
donor_data <- data_scm %>% 
  filter(!Country.Name %in% c("Iraq", "Liberia", "Haiti")) %>% 
  group_by(Country.Name) %>% 
  summarise(across(all_of(c(key_conflict_vars, key_economic_vars)), mean, na.rm = TRUE)) %>% 
  ungroup()

# Standardize both Iraq's data and the donor countries' data
iraq_standardized <- iraq_data %>% mutate(across(everything(), rescale))
donor_standardized <- donor_data %>%
  mutate(across(all_of(c(key_conflict_vars, key_economic_vars)), rescale))

# Apply weights to conflict and economic variables
donor_weighted <- donor_standardized %>%
  mutate(across(all_of(key_conflict_vars), ~ . * conflict_weight)) %>%
  mutate(across(all_of(key_economic_vars), ~ . * economic_weight))

iraq_weighted <- iraq_standardized %>%
  mutate(across(all_of(key_conflict_vars), ~ . * conflict_weight)) %>%
  mutate(across(all_of(key_economic_vars), ~ . * economic_weight))

# Compute the weighted Euclidean distance between Iraq and each donor
donor_data <- donor_weighted %>%
  rowwise() %>%
  mutate(distance = sqrt(sum((c_across(-Country.Name) - iraq_weighted)^2))) %>%
  ungroup()

# Define the range of years to keep (±5 years around the intervention year)
range_years <- pre_treatment_start:post_treatment_end

# Step 1: Find countries with complete data within the range of years
complete_countries <- data_scm %>%
  filter(year %in% range_years) %>%
  group_by(Country.Name) %>%
  filter(n() == length(range_years)) %>%
  pull(Country.Name)

# Step 2: Filter the donor_data for these complete countries
donor_data_filtered <- donor_data %>%
  filter(Country.Name %in% complete_countries)

# Select the top 5 most similar donor countries
selected_donors <- donor_data_filtered %>%
  arrange(distance) %>%
  slice_head(n = 10)

print(selected_donors)
```

Format Data for microsynth
```{r}
# Outcome vars will be c("GDP.current.US$", "total_FDI_n")
y <- c("GDP.current.US$", "total_FDI_n")
x <- c(
    "GDP.growth.annual.pct",  
#    "Foreign.direct.investment.net.inflows.pct.of.GDP", #factor that goes into the calculation with total FDI
#    "GDP.current.US$",   #factor that goes into the calculation with total FDI
#    "total.passengers.in",   #remove the airport-related variables to prevent endogeneity                 
#    "total.passengers.out",                   
#    "total.flights.in",                       
#    "total.flights.out",                      
#    "total.freight.in",                       
#    "total.freight.out",                      
#    "count.events.y.Battles",                 #iraq sadly has no ACLED data for this period
#    "count.events.y.Protests",                
#    "count.events.y.Explosions/Remote.violence",  
#    "count.events.y.Strategic.developments",   
#    "count.events.y.Violence.against.civilians",  
#    "fatalities.y.Battles",                   
#    "fatalities.y.Protests",                  
#    "fatalities.y.Explosions/Remote.violence",  
#    "fatalities.y.Strategic.developments",    
#    "fatalities.y.Violence.against.civilians",  
    "Services.value.added.pct.of.GDP",
    "Agriculture.forestry.and.fishing.value.added.pct.of.GDP",
    "Merchandise.trade.pct.of.GDP",
    "Mineral.rents.pct.of.GDP",
    "Services.value.added.pct.of.GDP",
    "GDP per capita, PPP (constant 2017 international $)",
    "GDP, PPP (constant 2017 international $)")

# Because we're not matching exactly, we will use match.out.min rather than match.out

donor_countries <- unique(selected_donors$Country.Name)
combined_countries <- sort(unique(c(iraq_country, donor_countries)))

year_range <- (intervention_year - 5):(intervention_year + 5)

sea1 <- microsynth(as.data.frame(long_data), idvar="Country.Name", timevar="year", intvar="Treatment",
             start.pre=pre_treatment_start, end.pre=(intervention_year-1), end.post=post_treatment_end,
             match.out = FALSE,
             match.out.min = x,
             match.covar = FALSE,
             result.var= y, omnibus.var=TRUE,
             test="lower", use.survey = FALSE, 
             max.mse = 10,
             perm=0, jack = 0, check.feas=TRUE, use.backup = TRUE,
             cal.epsilon = 0.01,
             n.cores = min(parallel::detectCores(), 2))
summary(sea1)

plot_microsynth(sea1)
```

