---
title: 'Data Tidying'
author: "Michelle Schultze"
date: "2024-02-02"
output:
  pdf_document: default
  html_document:
    df_print: paged
  word_document: default
---

```{r packages, message=FALSE, warning=FALSE}
library(tidyverse)
library(dplyr)
library(readr)
library(readxl)

#ACLED <- read_csv("data/ACLED index/ACLED_master.csv")
```

Bring in ACLED index data. (Takes 2 mins)
```{r ACLED-merge}
# merge ACLED sets together (had to be downloaded in segments)
ACLED1 <- read_csv("data/ACLED index/1997-01-01-2001-01-01.csv")
ACLED2 <- read_csv("data/ACLED index/2001-01-01-2011-01-01.csv")
ACLED3 <- read_csv("data/ACLED index/2011-01-01-2017-01-01.csv")
ACLED4 <- read_csv("data/ACLED index/2017-01-01-2018-01-01.csv")
ACLED5 <- read_csv("data/ACLED index/2018-01-01-2019-01-01.csv")
ACLED6 <- read_csv("data/ACLED index/2019-01-01-2021-01-01.csv")
ACLED7 <- read_csv("data/ACLED index/2021-01-01-2023-01-01.csv")
ACLED8 <- read_csv("data/ACLED index/2023-01-01-2024-01-01.csv")
ACLED <- full_join(ACLED1, full_join(ACLED2, full_join(ACLED3, full_join(ACLED4, full_join(ACLED5, full_join(ACLED6, full_join(ACLED7, ACLED8)))))))

#Check to make sure all observations are unique in the merged set
group_by(ACLED, event_id_cnty) %>%
  summarize(n_id = n()) %>%
  arrange(descending = TRUE)
# true — no repeats

write.csv(ACLED, "data/ACLED index/ACLED_master.csv")
```

Pivot other sets into usable format.
```{r pivot-econ-sets}
WB_businesses <- read.csv("data/WB_businesses.csv")
WB_businesses <- pivot_longer(data = WB_businesses, cols = 5:67, names_to = "year")
WB_businesses$year <- gsub("^.{0,1}", "", WB_businesses$year)

WB_economic_indicators <- read_excel("data/WB_economic_indicators.xlsx", .name_repair = "universal") 
WB_economic_indicators <- pivot_longer(data = WB_economic_indicators, cols = 5:67, names_to = "year")
WB_economic_indicators$year <- gsub("^.{0,3}", "", WB_economic_indicators$year)
WB_economic_indicators <- WB_economic_indicators %>%
  mutate(value = as.numeric(value))

WB_airports <- read.csv("data/airport_volume_airport_locations_WB.csv") %>%
  mutate(year = 2023)
```

Merge into a comprehensive country/year dataset.
```{r merge-econ-sets}
WB_economic_indicators <- WB_economic_indicators %>%
  mutate(Indicator.Name = Series.Name, Indicator.Code = Series.Code) %>%
  select(-Series.Name, -Series.Code) %>%
  relocate(year, .after = last_col()) %>%
  relocate(value, .after = last_col())

bigset <- full_join(WB_economic_indicators, WB_businesses)

#checking to make sure it added the variable
bigset %>%
  filter(Indicator.Name == "New businesses registered (number)")
#we're good

WB_airports2 <- WB_airports %>%
  group_by(Country.Name) %>%
  summarize(AirportsCount = n(),
            AirportsVolume = sum(TotalSeats),
            year = mean(year)) 

#testing to make sure the variables work and are sortable
WB_airports2 %>%
  arrange(AirportsVolume) 
#great

WB_airports3 <- pivot_longer(data = WB_airports2, cols = 2:3, names_to = "Indicator.Name") 
bigset <- bigset %>%
  mutate(year = as.numeric(year))
bigset <- full_join(bigset, WB_airports3)

#checking to make sure it added the variable
bigset %>%
  filter(Indicator.Name == "AirportsVolume")
#we're good
```

Aggregate and merge ACLED indicators
```{r ACLED-tidy}
ACLED2 <- ACLED %>%
  mutate(event_date = as.Date(ACLED$event_date, "%d %B %Y"))

ACLED_day <- ACLED2 %>%
  group_by(event_date, country) %>%
  count()

#aggregating by month and year
ACLED_month_total <- ACLED2 %>%
    group_by(month = lubridate::floor_date(event_date, 'month'),
             country) %>%
    summarize(fatalities_m = sum(fatalities),
              count_events_m = n()) %>%
  mutate(type = "All types of violent conflict")

ACLED_year_total <- ACLED_month_total %>%
    group_by(year = lubridate::floor_date(month, 'year'),
             country) %>%
    summarize(fatalities_y = sum(fatalities_m),
              count_events_y = sum(count_events_m))  %>%
  mutate(type = "All types of violent conflict")

#aggregating by type of conflict as well, adding to set
ACLED_month_types <- ACLED2 %>%
    group_by(month = lubridate::floor_date(event_date, 'month'),
             country, event_type) %>%
    summarize(fatalities_m = sum(fatalities),
              count_events_m = n(),
              type = event_type[1]) %>%
  select(-event_type)

ACLED_month <- full_join(ACLED_month_total, ACLED_month_types)

ACLED_year_types <- ACLED2 %>%
    group_by(year = lubridate::floor_date(event_date, 'year'),
             country, event_type) %>%
    summarize(fatalities_y = sum(fatalities),
              count_events_y = n(),
              type = event_type[1]) %>%
  select(-event_type)

ACLED_year <- full_join(ACLED_year_total, ACLED_year_types)

#prep to merge year-aggregated set with bigset 
#transform dates to readable/mergeable form
ACLED_month <- ACLED_month %>%
  mutate(month = format(month, "%b %Y"))

ACLED_year <- ACLED_year %>%
  mutate(year = format(year, "%Y"))

#pivot to long format and rename vars
ACLED_year <- ACLED_year %>% 
  pivot_longer(cols = 3:4, names_to = "Indicator.Name", values_to = "value") %>%
  mutate(Country.Name = country,
         Indicator.Name = paste0(Indicator.Name, ", ", type)) %>%
  select(-type, -country)

ACLED_month <- ACLED_month %>% 
  pivot_longer(cols = 3:4, names_to = "Indicator.Name", values_to = "value") %>%
  mutate(Country.Name = country,
         Indicator.Name = paste0(Indicator.Name, ", ", type)) %>%
  select(-type, -country)

#merge yearly set with bigset
bigset <- bigset %>% 
  mutate(year = as.character(year)) %>%
  full_join(ACLED_year)

#check merge
bigset %>%
  filter(Indicator.Name == "count_events_y, Protests")
#good
```

Isolate spellings that don't match
```{r spellings}
bigset %>%
  group_by(Country.Name) %>%
  summarize(Count = n()) %>%
  filter(Count < 100) %>%
  print(n = 50)

#search df
bigset %>%
  filter(grepl('tristan', Country.Name))

bigset <- bigset %>%
  mutate(Country.Name = case_when(
    Country.Name == "Democratic Republic of the Congo" ~ "Congo, Dem. Rep.",
    Country.Name == "Congo" ~ "Congo, Dem. Rep.",
    Country.Name == "Bahamas" ~ "Bahamas, The",
    Country.Name == "Cape Verde" ~ "Cabo Verde",
    Country.Name == "Czech Republic" ~ "Czechia",
    Country.Name == "East Timor" ~ "Timor-Leste",
    Country.Name == "Egypt" ~ "Egypt, Arab Rep.",
    Country.Name == "Gambia" ~ "Gambia, The", 
    Country.Name == "Guinea Bissau" ~ "Guinea-Bissau",
    Country.Name == "Iran" ~ "Iran, Islamic Rep.",
    Country.Name == "Ivory Coast (Cote d'Ivoire)" ~ "Cote d'Ivoire",
    Country.Name == "Kyrgyzstan" ~ "Kyrgyz Republic", 
    Country.Name == "Laos" ~ "Lao PDR",
    Country.Name == "Macedonia" ~ "North Macedonia",
    Country.Name == "Micronesia" ~ "Micronesia, Fed. Sts.",
    Country.Name == "North Korea" ~ "Korea, Dem. People's Rep.", 
    Country.Name == "Saint Kitts and Nevis" ~ "St. Kitts and Nevis",
    Country.Name == "Saint Lucia" ~ "St. Lucia",
    Country.Name == "Saint Vincent and Grenadines" ~ "St. Vincent and the Grenadines",
    Country.Name == "Saint Vincent and the Grenadines" ~ "St. Vincent and the Grenadines",
    Country.Name == "Slovakia" ~ "Slovak Republic",
    Country.Name == "South Korea" ~ "Korea, Rep.",
    Country.Name == "Swaziland" ~ "Eswatini",
    Country.Name == "Syria" ~ "Syrian Arab Republic",
    Country.Name == "Yemen" ~ "Yemen, Rep.",
    Country.Name == "Vietnam" ~ "Viet Nam",
    Country.Name == "Venezuela" ~ "Venezuela, RB",
    Country.Name == "Turkey" ~ "Turkiye",
    Country.Name == "Hong Kong (SAR)" ~ "Hong Kong SAR, China",
    Country.Name == "Macau (SAR)" ~ "Macao SAR, China",
    Country.Name == "Brunei" ~ "Brunei Darussalam",
    Country.Name == "West Bank and Gaza" ~ "Palestine",
    Country.Name == "Russia" ~ "Russian Federation",
    Country.Name == "Saint Martin" ~ "St. Martin (French part)",
    Country.Name == "Saint-Martin" ~ "St. Martin (French part)",
    Country.Name == "Sint Maarten" ~ "Sint Maarten (Dutch part)",
    Country.Name == "Saint-Barthelemy" ~ "Saint Barthelemy",
    TRUE ~ Country.Name)
  ) %>%
  filter(!(Country.Name %in% c("European Union", "Latin America & Caribbean", "Latin America & Caribbean (excluding high income)", "South Asia", "Sub-Saharan Africa (excluding high income)", "Grenada and South Grenadines", "Saint Helena, Ascension and Tristan da Cunha")))
# "grenada and south grenadines" overlap between country observations -- drop to be safe
# WB does not recognize Taiwan unfortunately

bigset %>%
  group_by(Country.Name) %>%
  summarize(Count = n()) %>%
  filter(Count < 150) %>%
  print(n = 50)
#Remainder are very small and isolated territories of other countries or unrecognized by WB as countries -- better to keep as their own entries
#Keep consistent labels for ease of adding other data if needed
```

Save our tidied datasets for further use
```{r writecsvs}
write.csv(bigset, "data/master_dataset.csv")
write.csv(ACLED_month, "data/ACLED_month.csv")
```

Merge flight data 
(Downloaded from https://www.bts.gov/browse-statistical-products-and-data/bts-
publications/data-bank-28im-t-100-and-t-100f-internationa-0)
```{r merge-flights}
# Set the working directory to where the data files are located
setwd("/Users/michelle/Documents/UKR-airports/data/flights/transportation statistics data/multiple years")

# List all .asc files in the directory
file_list <- list.files(pattern = "\\.asc$")

# Initialize an empty list to store data frames
data_list <- list()

# Function to handle missing values and remove the first row (header)
clean_data <- function(data) {
  # Remove first row (header) and convert it to column names
  col_names <- data[1, ]
  data <- data[-1, ]
  colnames(data) <- col_names
  
  # Replace "NA" strings with actual NA values
  data[data == "NA"] <- NA
  return(data)
}

# Loop through each file, read it, clean the data, and append it to the data list
for (file in file_list) {
  data <- read.csv(file, header = FALSE, sep = "|", stringsAsFactors = FALSE)
  data <- clean_data(data)
  
  # Only add the dataframe to data_list if it has the expected number of columns (20)
  if (ncol(data) == 20) {
    data_list[[file]] <- data
  } else {
    cat("Skipping file", file, "due to irregular dimensions.\n")
  }
}

# Combine all data frames into one if there are any
if (length(data_list) > 0) {
  # Combine all data frames into one
  full_data <- do.call(rbind, data_list)
  
  # Convert numeric columns from character to numeric
  num_cols <- c("Year", "Month", "Origin_Airport_ID", "Destination_Airport_ID", "Flight_Number", "Scheduled_Departures", "Scheduled_Seats", "Flights_Cancelled", "Flights_Diverted", "Scheduled_Passengers", "Actual_Passengers", "Flights_Departed", "Payload", "Seats", "Freight")
  full_data[, num_cols] <- lapply(full_data[, num_cols], as.numeric)
  
  # Optionally, you can save the merged dataset to a CSV file
  # write.csv(full_data, "merged_data.csv", row.names = FALSE)
  
  # Check the structure of the merged dataset
  str(full_data)
} else {
  cat("No valid data frames found. Check your data files for issues.")
}

# Adjust num_cols based on the actual column names
num_cols <- c("year", "month", "origin_wac", "origin_city_market_id", "dest_wac", "dest_city_market_id", "distance", "passengers", "freight", "mail")

# Convert numeric columns from character to numeric
full_data[, num_cols] <- lapply(full_data[, num_cols], as.numeric)

# Check the structure of the merged dataset
str(full_data)



# Adjust num_cols based on the actual column names, excluding the "NA" column
num_cols <- c("year", "month", "origin_wac", "origin_city_market_id", "dest_wac", "dest_city_market_id", "distance", "passengers", "freight", "mail")

# Remove "NA" from the column names
full_data <- full_data[, !colnames(full_data) %in% "NA"]

# Convert numeric columns from character to numeric
full_data[, num_cols] <- lapply(full_data[, num_cols], as.numeric)

# Check the structure of the merged dataset
str(full_data)

```

Extract country variables from city columns
```{r country-variables}
# Function to extract country information
extract_country <- function(city_name) {
  # Split the city name by comma
  parts <- strsplit(city_name, ",")[[1]]
  
  # Extract the last part as the country
  country <- trimws(parts[length(parts)])
  
  # Convert state codes to "USA"
  if (country %in% state_codes) {
    country <- "USA"
  }
  
  return(country)
}

# Define a vector of 2-letter state codes
state_codes <- c("AL", "AK", "AZ", "AR", "CA", "CO", "CT", "DE", "FL", "GA", 
                 "HI", "ID", "IL", "IN", "IA", "KS", "KY", "LA", "ME", "MD", 
                 "MA", "MI", "MN", "MS", "MO", "MT", "NE", "NV", "NH", "NJ", 
                 "NM", "NY", "NC", "ND", "OH", "OK", "OR", "PA", "RI", "SC", 
                 "SD", "TN", "TX", "UT", "VT", "VA", "WA", "WV", "WI", "WY", 
                 "DC", "TT", "PR", "VI")

#Trust territories were administered by the US until this code stopped being used

# Create origin country column
full_data$origin_country <- sapply(full_data$origin_city_name, extract_country)

# Create destination country column
full_data$destination_country <- sapply(full_data$dest_city_name, extract_country)

# Display the first few rows of the updated dataset
head(full_data)

```

Aggregate by country and month
```{r aggregate-flights}
x <- full_data %>%
  group_by(year, month, origin_country, destination_country) %>%
  summarize(total_passengers = sum(passengers),
            total_freight = sum(freight),
            total_mail = sum(mail),
            total_flights = n())

#testing for irregularities
x %>% 
  group_by(origin_country, destination_country, year, month) %>%
  count() %>%
  filter(n > 1)
#Great, no double counting

#making sure trust territories carried over properly
x %>% 
  group_by(origin_country, destination_country, year, month) %>%
  count() %>%
  filter(origin_country == "Palau" | destination_country == "Palau") %>%
  arrange(year)
#yes, these start being recorded in 1994, when it entered in free association with the US

#export
write.csv(x, "/Users/michelle/Documents/UKR-airports/data/flights_master.csv")
#x <- read.csv("/Users/michelle/Documents/UKR-airports/data/flights_master.csv")
```

Reshape flights dataset
```{r reshape-flights}
y <- x %>% 
  mutate(country = case_when(origin_country != "USA" ~ origin_country,
                             destination_country != "USA" ~ destination_country),
         in_out = case_when(origin_country != "USA" ~ "out",
                             destination_country != "USA" ~ "in")) %>%
  mutate(total_freight_in = case_when(in_out == "out" ~ 0,
                                       in_out == "in" ~ total_freight),
         total_freight_out = case_when(in_out == "in" ~ 0,
                                       in_out == "out" ~ total_freight),
         total_mail_in = case_when(in_out == "out" ~ 0,
                                       in_out == "in" ~ total_mail),
         total_mail_out = case_when(in_out == "in" ~ 0,
                                       in_out == "out" ~ total_mail),
         total_passengers_in = case_when(in_out == "out" ~ 0,
                                       in_out == "in" ~ total_passengers),
         total_passengers_out = case_when(in_out == "in" ~ 0,
                                       in_out == "out" ~ total_passengers),
         total_flights_in = case_when(in_out == "out" ~ 0,
                                       in_out == "in" ~ total_flights),
         total_flights_out = case_when(in_out == "in" ~ 0,
                                       in_out == "out" ~ total_flights)) %>%
  group_by(country, year, month) %>%
  summarize(total_freight_in = sum(total_freight_in),
            total_freight_out = sum(total_freight_out),
            total_mail_in = sum(total_mail_in),
            total_mail_out = sum(total_mail_out),
            total_passengers_in = sum(total_passengers_in),
            total_passengers_out = sum(total_passengers_out),
            total_flights_in = sum(total_flights_in),
            total_flights_out = sum(total_flights_out))
#"in" describes into the country of interest, not into the US
```

Complete all rows in the dataset not included (nulls)
```{r complete-flights}
library(tidyr)

# Convert factor columns to character or numeric
y$country <- as.character(y$country)
y$year <- as.numeric(y$year)
y$month <- as.numeric(y$month)

# Create a data frame with all combinations of country, year, and month
all_combinations <- expand.grid(
  country = unique(y$country),
  year = unique(y$year),
  month = unique(y$month)
)

# Merge or join all_combinations with your original data
complete_data <- merge(all_combinations, y, by = c("country", "year", "month"), all.x = TRUE)

# Fill missing values with 0
complete_data[is.na(complete_data)] <- 0

#Check to make sure it loaded properly
complete_data %>%
  filter(total_freight_in != 0 &
         total_freight_out != 0 &
         total_mail_in != 0 &
         total_mail_out != 0 &
         total_passengers_in != 0 &
         total_passengers_out != 0 &
         total_flights_in != 0 &
         total_flights_out != 0) %>%
  group_by(country) %>%
  count() %>%
  arrange(-n)

y %>%
  filter(total_freight_in != 0 &
         total_freight_out != 0 &
         total_mail_in != 0 &
         total_mail_out != 0 &
         total_passengers_in != 0 &
         total_passengers_out != 0 &
         total_flights_in != 0 &
         total_flights_out != 0) %>%
  group_by(country) %>%
  count() %>%
  arrange(-n)

#They're the same. Success :)

y <- complete_data
```

Generate "change in" variables
```{r change-flights}
# Group by country and year, then calculate the percentage change
y_changes <- y %>%
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(
    flights_in_change_pct = ifelse(lag(total_flights_in) != 0, ((total_flights_in - lag(total_flights_in)) / lag(total_flights_in)) * 100, NA),
    passengers_in_change_pct = ifelse(lag(total_passengers_in) != 0, ((total_passengers_in - lag(total_passengers_in)) / lag(total_passengers_in)) * 100, NA),
    mail_in_change_pct = ifelse(lag(total_mail_in) != 0, ((total_mail_in - lag(total_mail_in)) / lag(total_mail_in)) * 100, NA),
    freight_in_change_pct = ifelse(lag(total_freight_in) != 0, ((total_freight_in - lag(total_freight_in)) / lag(total_freight_in)) * 100, NA),
    flights_out_change_pct = ifelse(lag(total_flights_out) != 0, ((total_flights_out - lag(total_flights_out)) / lag(total_flights_out)) * 100, NA),
    passengers_out_change_pct = ifelse(lag(total_passengers_out) != 0, ((total_passengers_out - lag(total_passengers_out)) / lag(total_passengers_out)) * 100, NA),
    mail_out_change_pct = ifelse(lag(total_mail_out) != 0, ((total_mail_out - lag(total_mail_out)) / lag(total_mail_out)) * 100, NA),
    freight_out_change_pct = ifelse(lag(total_freight_out) != 0, ((total_freight_out - lag(total_freight_out)) / lag(total_freight_out)) * 100, NA)
  ) %>%
  mutate(
    flights_in_change_pct = ifelse(is.na(flights_in_change_pct), 0, flights_in_change_pct),
    passengers_in_change_pct = ifelse(is.na(passengers_in_change_pct), 0, passengers_in_change_pct),
    mail_in_change_pct = ifelse(is.na(mail_in_change_pct), 0, mail_in_change_pct),
    freight_in_change_pct = ifelse(is.na(freight_in_change_pct), 0, freight_in_change_pct),
    flights_out_change_pct = ifelse(is.na(flights_out_change_pct), 0, flights_out_change_pct),
    passengers_out_change_pct = ifelse(is.na(passengers_out_change_pct), 0, passengers_out_change_pct),
    mail_out_change_pct = ifelse(is.na(mail_out_change_pct), 0, mail_out_change_pct),
    freight_out_change_pct = ifelse(is.na(freight_out_change_pct), 0, freight_out_change_pct)
  ) 

```

Regenerate flight data in aggregated per-year form
```{r year-flights}
# Group by country and year, then calculate the percentage change
z <- y %>%
  pivot_longer(cols = 4:11, names_to = "Indicator.Name") 

z <- z %>%
    group_by(country, year, Indicator.Name) %>%
    summarize(value = sum(value)) 

zz <- z %>% 
  pivot_wider(names_from = Indicator.Name, values_from = value)

#PROB FOR TODAY: fix it above so that you can pivot it after this and don't have to worry about rewriting the code chunk
z_changes <- zz %>%
  arrange(country, year) %>%
  group_by(country) %>%
  mutate(
    flights_in_change_pct = ifelse(lag(total_flights_in) != 0, ((total_flights_in - lag(total_flights_in)) / lag(total_flights_in)) * 100, NA),
    passengers_in_change_pct = ifelse(lag(total_passengers_in) != 0, ((total_passengers_in - lag(total_passengers_in)) / lag(total_passengers_in)) * 100, NA),
    mail_in_change_pct = ifelse(lag(total_mail_in) != 0, ((total_mail_in - lag(total_mail_in)) / lag(total_mail_in)) * 100, NA),
    freight_in_change_pct = ifelse(lag(total_freight_in) != 0, ((total_freight_in - lag(total_freight_in)) / lag(total_freight_in)) * 100, NA),
    flights_out_change_pct = ifelse(lag(total_flights_out) != 0, ((total_flights_out - lag(total_flights_out)) / lag(total_flights_out)) * 100, NA),
    passengers_out_change_pct = ifelse(lag(total_passengers_out) != 0, ((total_passengers_out - lag(total_passengers_out)) / lag(total_passengers_out)) * 100, NA),
    mail_out_change_pct = ifelse(lag(total_mail_out) != 0, ((total_mail_out - lag(total_mail_out)) / lag(total_mail_out)) * 100, NA),
    freight_out_change_pct = ifelse(lag(total_freight_out) != 0, ((total_freight_out - lag(total_freight_out)) / lag(total_freight_out)) * 100, NA)
  ) %>%
  mutate(
    flights_in_change_pct = ifelse(is.na(flights_in_change_pct), 0, flights_in_change_pct),
    passengers_in_change_pct = ifelse(is.na(passengers_in_change_pct), 0, passengers_in_change_pct),
    mail_in_change_pct = ifelse(is.na(mail_in_change_pct), 0, mail_in_change_pct),
    freight_in_change_pct = ifelse(is.na(freight_in_change_pct), 0, freight_in_change_pct),
    flights_out_change_pct = ifelse(is.na(flights_out_change_pct), 0, flights_out_change_pct),
    passengers_out_change_pct = ifelse(is.na(passengers_out_change_pct), 0, passengers_out_change_pct),
    mail_out_change_pct = ifelse(is.na(mail_out_change_pct), 0, mail_out_change_pct),
    freight_out_change_pct = ifelse(is.na(freight_out_change_pct), 0, freight_out_change_pct)
  ) 

z <- z_changes %>%
  pivot_longer(cols = 3:18, names_to = "Indicator.Name") %>%
  mutate(Country.Name = country) %>%
  ungroup() %>%
  select(-country)
```

Merge with master dataset
```{r merge-flights-master}
master_dataset <- read_csv("data/master_dataset.csv")

alpha <- master_dataset %>%
  merge(z, by = c("Country.Name", "year", "Indicator.Name", "value"), 
        all.x = TRUE, all.y = TRUE) 

alpha[, -5]

#export new master set
write.csv(alpha, "/Users/michelle/Documents/UKR-airports/data/master_dataset.csv")
```



Quantile regression
```{r}
library(quantreg)




z <- y_changes %>%
  merge(ACLED, all = TRUE) 

rqfit <- rq(mpg ~ passengers_in_change_pct, data = mtcars)
rqfit
summary(rqfit)

plot(mpg ~ wt, data = mtcars, pch = 16, main = "mpg ~ wt")
abline(lm(mpg ~ wt, data = mtcars), col = "red", lty = 2)
abline(rq(mpg ~ wt, data = mtcars), col = "blue", lty = 2)
legend("topright", legend = c("lm", "rq"), col = c("red", "blue"), lty = 2)
```


Generate proportion variables (% passengers going in, % flights going in, etc)
```{r}
#tba
```


Sources:
In the interest of saving time, some of the importing/tidying/merging code was
generated by ChatGPT and modified to fit the needs of this project. The 
remainder was coded by hand, referencing Stack Overflow and other online forums.
